% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\documentclass[
]{article}
\usepackage{xcolor}
\usepackage{amsmath,amssymb}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\newenvironment{Shaded}{}{}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{1.00,0.00,0.00}{\textbf{#1}}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{#1}}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.49,0.56,0.16}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{#1}}
\newcommand{\BuiltInTok}[1]{\textcolor[rgb]{0.00,0.50,0.00}{#1}}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textit{#1}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{#1}}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.53,0.00,0.00}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.00,0.44,0.13}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.56,0.13,0.00}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.73,0.13,0.13}{\textit{#1}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{1.00,0.00,0.00}{\textbf{#1}}}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.02,0.16,0.49}{#1}}
\newcommand{\ImportTok}[1]{\textcolor[rgb]{0.00,0.50,0.00}{\textbf{#1}}}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{#1}}}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.00,0.44,0.13}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{#1}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.40,0.40,0.40}{#1}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.00,0.44,0.13}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.74,0.48,0.00}{#1}}
\newcommand{\RegionMarkerTok}[1]{#1}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.73,0.40,0.53}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.10,0.09,0.49}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{#1}}}}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\author{}
\date{}

\begin{document}

\section{MINIF2F: A CROSS-SYSTEM BENCHMARK FOR FORMAL OLYMPIAD-LEVEL
MATHEMATICS}\label{minif2f-a-cross-system-benchmark-for-formal-olympiad-level-mathematics}

Kunhao Zheng

École Polytechnique

kunhao.zheng@polytechnique.edu

Jesse Michael Han

OpenAI

University of Pittsburgh

jessemichaelhan@openai.com

Stanislas Polu

OpenAI

spolu@openai.com

\section{ABSTRACT}\label{abstract}

We present miniF2F, a dataset of formal Olympiad-level mathematics
problems statements intended to provide a unified cross-system benchmark
for neural theorem proving. The miniF2F benchmark currently targets
Metamath, Lean, Isabelle (partially) and HOL Light (partially) and
consists of 488 problem statements drawn from the AIME, AMC, and the
International Mathematical Olympiad (IMO), as well as material from
high-school and undergraduate mathematics courses. We report baseline
results using GPT-f (Polu \& Sutskever, 2020), a neural theorem prover
based on GPT-3 (Brown et al., 2020) and provide an analysis of its
performance. We intend for miniF2F to be a community-driven effort and
hope that our benchmark will help spur advances in neural theorem
proving.

\section{1 INTRODUCTION}\label{introduction}

Shared benchmarks and datasets have historically played a crucial role
in driving advances in large-scale applications of deep learning,
e.g.~in computer vision (Deng et al., 2009) and natural language
processing (Wang et al., 2019; Rajpurkar et al., 2016; Paperno et al.,
2016). Neural theorem proving is a rapidly developing area which aims to
apply techniques from deep learning to interactive theorem proving. To
date, most contributions in this area have focused on individual theorem
proving systems, each with a separately-implemented mathematics library
and with results reported on a dataset-specific test split; examples
include the HOList (Bansal et al., 2019a), CoqGym (Yang \& Deng, 2019)
and LeanStep (Han et al., 2021) theorem proving environments and
benchmarks. However, benchmarks from this paradigm are not ideal for
measuring the mathematical reasoning ability of neural theorem provers
for several reasons. Library-specific train/test splits are siloed by
construction, dependent on how theorems and lemmas are split in these
libraries, and as such are not directly comparable across systems.
Moreover, formal mathematics libraries are closer to software
repositories than informal mathematical exposition, and many lemmas are
implementation-specific artifacts without precise informal mathematical
or cross-system translations.

To date, the neural theorem proving community has not organized its
efforts around a cross-system benchmark. To address this need and to
provide a common resource to research groups working on formal theorem
proving, we present miniF2F, a unified cross-system benchmark of formal
mathematics of progressively increasing difficulty, centering around
Olympiad-level problem statements (AMC, AIME, IMO) as well as
high-school and undergraduate maths classes. Both the content and name
of miniF2F are inspired by the IMO Grand Challenge (Selsam et al.,
2019): to build an AI that can win a gold medal in the International
Mathematical Olympiad in a formal-to-formal (F2F) format. More
precisely, the agent must receive IMO problems written in a formal
mathematical format, and must produce a formal (i.e.~machine-checkable)
proof for that problem.

We intend for miniF2F to serve as a stepping stone for different formal
systems towards the IMO Grand Challenge (Selsam et al., 2019), as it is
end-to-end verifiable, cross-platform and spans a wide range of
difficulty. While we report baseline results on miniF2F using GPT-f, a
language model

based on GPT-3 which has been finetuned for theorem proving, language
models are not a mandatory approach for Olympiad problems and this
assumption is not reflected in miniF2F, preserving the generality and
widespread applicability of the benchmark to systems similar to DeepHOL
(Bansal et al., 2019a) or Holophrasm (Whalen, 2016).

\section{2 BACKGROUND AND RELATED
WORK}\label{background-and-related-work}

\section{BENCHMARKS}\label{benchmarks}

In the closely related field of (first-order) automated theorem proving
(ATP), the TPTP (Sutcliffe, 2017) benchmark is a library of test
problems in a unified format for ATP systems. In interactive theorem
proving, the ``Freek 100'' (Wiedijk, 2008) tracks progress across
various interactive theorem provers on a list of 100 mathematical
theorems. Wu et al.~(2021) built a simplified formal proof environment
INT with an associated synthetic inequality benchmark. Competitions and
communal challenges have also spurred development in formal theorem
proving. The CADE ATP System Competition (CASC) (Sutcliffe, 2016) is a
competition that evaluates the performance of first-order automated
theorem proving systems. Proof Ground (Haslbeck et al., 2019), part of
the ITP conference, is an interactive proving contest (for humans) that
supports Coq, Isabelle, and Lean, which focuses on evaluating the
formalization effort of proof to given problems within limited time.
Finally, the IMO Grand Challenge (Selsam et al., 2019), a proposal from
researchers working on the interactive proof assistant Lean, aims to
build a system capable of solving IMO problems in the formal-to-formal
format.

Due to its convenient framing as a natural language processing task, the
domain of informal mathematical reasoning has received more attention
than the formal one. MATH (Hendrycks et al., 2021) is a mathematics
benchmark comprising 12,500 statements in natural language where
exercises are classified into 5 levels of difficulty across various
domains. Each exercise is combined with a detailed step-by-step proof in
natural language. Scaling state-of-the-art models shows little
amelioration on MATH, which requires advanced mathematical reasoning
capabilities. miniF2F includes a number of formalized statements from
MATH. NaturalProofs (Welleck et al., 2021) is another benchmark of
natural proof in mathematics, containing 32k theorem statements and
proofs. It essentially contains the proofs in ProofWiki and other
resources. While MATH is more oriented towards mathematics exercises,
NaturalProofs is focused on proofs of general mathematics theorems.
Saxton et al.~(2019) built a mathematics dataset with
\(2 \times 10^{6}\) training data and \(10^{4}\) test data, presented in
a question-answering format where each statement is paired with a
question written in natural language and a direct answer without proof.

\section{NEURAL THEOREM PROVING}\label{neural-theorem-proving}

HOList (Bansal et al., 2019a;b; Paliwal et al., 2020) provides an
environment as well as a benchmark for HOL Light. They also proposes
various deep reinforcement learning approaches for theorem proving and
report a pass rate of 59.91\% on their benchmark. Yang \& Deng (2019)
built CoqGym, a large-scale dataset, which comes also with a learning
environment, of 71k human-written proofs in Coq proof assistant. They
report a 30.0\% pass rate on the held-out test theorems in CoqGym. Polu
\& Sutskever (2020) applied a decoder-only transformer similar to GPT-3
(Brown et al., 2020) to proof steps prediction in Metamath combined with
a log-probability based proof search. They also proposed a methodology
to train a value function to further guide proof search, achieving a
56.22\% pass rate on the held-out test set. Large language models were
applied to Lean by Han et al.~(2021). They created an environment around
the Lean prover targeted to machine learning and propose a dataset
extracted from low level proof artifacts that is shown to boost
performance when used as a self-supervised co-training objective. They
report a 48.4\% pass rate on held-out test statements from mathlib,
Lean's mathematical library (mathlib Community, 2020).

\section{3 MINIF2F BENCHMARK}\label{minif2f-benchmark}

miniF2F is a dataset of manually formalized statements of Olympiad type
problems, aligned in Lean, Metamath, and Isabelle (partial at the time
of writing), providing a cross-platform benchmark for formal
mathematical reasoning. Olympiad type problems are of particular
interest to compare

Table 1: Number of statements and their provenance in miniF2F v1

TOTAL

244

244

IMO

20

20

AIME

15

15

AMC

45

45

MATH

Algebra

Level 5

14

14

Level 4

14

14

Level 3

14

14

Level 2

14

14

Level 1

14

14

Number Theory

Level 5

16

16

Level 4

11

11

Level 3

11

11

Level 2

11

11

Level 1

11

11

CUSTOM

Algebra

18

18

Number Theory

8

8

Induction

8

8

automated provers across different formal systems as the theories
required to solve them are well identified and they generally do not
require the definition of new mathematical concepts (a capability that
remains beyond the current neural theorem proving state of the art).

The formalized statements in miniF2F are drawn from multiple sources,
ranging from high school and undergraduate level exercises to Olympiad
problems. miniF2F also covers different sub-subjects in mathematics as
well as proof strategies, focusing on the types of exercises whose
statements are expressible in most formal systems. This leads to a
systemic focus on algebra, number theory and inequalities because, for
example, geometry and combinatorial problems are generally challenging
to formalize due to only nascent efforts in these areas in most formal
systems. The statements in miniF2F are all manually formalized and
selected to cover a variety of difficulty levels for both humans and
machines. Formal proofs for these statements are optionally attached.

miniF2F draws from AIME, AMC, IMO problems as well as problems from the
MATH (Hendrycks et al., 2021) informal dataset. Formalizing problems
from the MATH dataset serves two purposes. First, problems in MATH are
segmented by difficulty level (from 1 to 5), randomly selecting a subset
from each of these difficulty levels allows miniF2F to cover a wider
range of difficulty. Second, it provides the community an opportunity to
compare capabilities of formal automated prover to their informal
counter-parts as discussed in later sections.

miniF2F comprises a test set and a validation set, which are a
stratified random split from the statements we formalized such that each
set equally covers each problem type and difficulty (when available).
Table 1 shows a detailed distribution of these statements.

Versioning miniF2F is an evolving effort and new statements will
continuously be added. Periodically, we will freeze versions of the
benchmark. The current version of the benchmark is v1 \(^{1}\) and
results in this paper are reported using this version. v1 comprises 244
test and 244 valid statements. The set of statements of each version is
guaranteed to remain stable, only allowing fixes in case errors are
later discovered.

Rules of engagement and License miniF2F is meant to serve as a shared
resource for research groups working on applying deep learning to formal
theorem proving. There is no formal process to submit evaluation results
and researchers are simply invited to cite miniF2F indicating the
version used in their evaluations. We also encourage them to contribute
proofs found by their approaches back to the benchmark. The parts of the
benchmark associated with each theorem prover (Metamath,

Lean, Isabelle) are meant to be licensed in a way that is aligned with
the licensing usage associated with the theorem prover's main library.
As a result, the Metamath version of the benchmark is released under the
MIT License, while the Lean and Isabelle versions are released under the
Apache License.

Formalization effort and challenges We found that, for trained
practitioners (but not necessarily experts, including students recently
introduced to formal systems), formalizing a statement takes about 15
minutes on average, and reviewing a formalized statement, about half of
that on average. Note that not all exercises are directly or naturally
formalizable. In particular, multi-choice questions, word problems, and
exercises that require to explicit a witness or a set as part of the
answer present interesting challenges:

multi-choice questions \(^{2}\) these problems are generally
straightforwardly formalizable by reformulating the statement using the
right answer only, and could be made ``fair'' in a competitive setup by
formalizing all possible choices and running automated provers on all of
them, attributing points only if a proof of the correct answer is
provided.

word problems \(^{3}\) where significant information is presented in
natural language generally require non-trivial efforts to be formalized.
We generally formalized them by explicitly modeling the mathematics
concepts and expression presented in natural language while attempting
as best as possible to preserve the mathematical difficulty of the
original problem. Sometime the formalization work is most of the
difficulty associated with the original question; in such cases we would
discard the problem entirely.

problems that require to explicit a set or witness \(^{4}\) (e.g.~find
all \ldots{} such that \ldots) are not directly formalizable. The best
approximation we relied on for these was to formalize the statement with
the witness or answer provided, turning such exercises into the
generation of a proof that the answer is correct, and if needed, that it
is the unique one---which is, at times, a much easier exercise. A non
negligible portion of IMO problems are as such, which we foresee could
become a challenge in the future, to fairly compare humans to automated
proving systems in a competitive setup.

Porting effort In addition to Metamath, Lean, Isabelle (work in
progress) and HOL Light (work in progress), we are eager to extend the
coverage of miniF2F to Coq, and will welcome any effort in that
direction or to extend miniF2F to further systems.

\section{4 EXPERIMENTS}\label{experiments}

In this section, in order to study baseline performances associated with
existing systems, we report pass rates achieved by GPT-f (Polu \&
Sutskever, 2020) applied to Metamath, GPT-f/PACT (Polu \& Sutskever,
2020; Han et al., 2021) applied to Lean as well as a baseline prover
implemented in Lean denoted as the tidy baseline. Pass rates are
reported as Pass@N where N is the number of proof search attempts per
statement. Pass@N is computed by running more attempts per statement,
averaged to get an unbiased, low-variance estimate.

\section{4.1 METAMATH}\label{metamath}

Metamath is powered by a meta logic system based on a single
substitution rule. It's characterized by its simplicity which makes it
convenient to study machine learning. Proofs in Metamath are, as a
consequence of the low-level proofsteps, much longer than in other
systems as there is no assistance from high-level tactics. Proofs which
are trivial in other systems (e.g.~n-digit addition or simple ring
arithmetic transformations) can be quite tedious in Metamath. The
absence of tactics is both

\textit{[Image omitted: images/bd8bc2759f3443632d7aaf0ce973d9d394201ead35ca67bab5734bcaa839b165.jpg]}

bar

miniF2F-valid and miniF2F-test \textbar{} Category \textbar{}
miniF2F-valid - metamath-gptf \textbar{} miniF2F-valid - tidy \textbar{}
miniF2F-valid - lean-gptf \textbar{} miniF2F-test - metamath-gptf
\textbar{} miniF2F-test - tidy \textbar{} miniF2F-test - lean-gptf
\textbar{} \textbar{} :--- \textbar{} :--- \textbar{} :--- \textbar{}
:--- \textbar{} :--- \textbar{} :--- \textbar{} :--- \textbar{}
\textbar{} IMO \textbar{} 0 \textbar{} 0 \textbar{} 0 \textbar{} 0
\textbar{} 0 \textbar{} 0 \textbar{} \textbar{} AIME \textbar{} 0
\textbar{} 0 \textbar{} 0 \textbar{} 0 \textbar{} 1 \textbar{} 2
\textbar{} \textbar{} AMC \textbar{} 0 \textbar{} 4 \textbar{} 8
\textbar{} 0 \textbar{} 3 \textbar{} 7 \textbar{} \textbar{} MATH
Algebra \textbar{} 1 \textbar{} 15 \textbar{} 32 \textbar{} 4 \textbar{}
22 \textbar{} 36 \textbar{} \textbar{} MATH Number Theory \textbar{} 0
\textbar{} 17 \textbar{} 25 \textbar{} 0 \textbar{} 18 \textbar{} 25
\textbar{} \textbar{} CUSTOM Algebra \textbar{} 2 \textbar{} 5
\textbar{} 6 \textbar{} 0 \textbar{} 0 \textbar{} 2 \textbar{}
\textbar{} CUSTOM Number Theory \textbar{} 2 \textbar{} 0 \textbar{} 2
\textbar{} 0 \textbar{} 0 \textbar{} 0 \textbar{} \textbar{} CUSTOM
Induction \textbar{} 0 \textbar{} 0 \textbar{} 0 \textbar{} 0 \textbar{}
0 \textbar{} 1 \textbar{}

Figure 1: Counts of successfully proved statements in miniF2F. Green
bar: results from Lean GPT-f.~Red bar: best result from the tidy
baseline. Blue bar: results from Metamath GPT-f.

a benefit, as the models sees and learns on everything, and a challenge,
as proofs of even simple exercises require hundreds of proofsteps.

\section{4.1.1 GPT-F}\label{gpt-f}

We report the pass rate of GPT-f applied to Metamath as described in
Polu \& Sutskever (2020). We use a model with 700m learnable parameters.
The model is trained on an updated dump of the set.mm library (but
similar synthetic datasets), using the log-probability based search as
reported in Table 8 of the GPT-f paper (Polu \& Sutskever, 2020).

The model achieves a Pass@1 of 1.3\% and a Pass@8 of 1.6\% on
miniF2F-test. As expected, these numbers are quite low due to the length
of typical proofs for even simple math exercises. The average proof
length is also reported in Table 3.

\section{4.2 LEAN}\label{lean}

In comparison to Metamath, Lean benefits from a large number of powerful
tactics to assist formalization efforts. Typical Lean proofs are much
shorter than Metamath's. This is also a formal system of interest as it
has received a lot of attention from the mathematical community as
recent theories have successfully been formalized in Lean (Perfectoid
Spaces (Buzzard et al., 2019), Liquid Tensor experiment (Scholze,
2020)).

Lean is also associated with the IMO Grand Challenge (Selsam et al.,
2019) which aims to organize a formal-to-formal challenge during the
upcoming IMO competitions.

\section{4.2.1 TIDY BASELINE}\label{tidy-baseline}

We use the generic best-first search algorithm presented in PACT (Han et
al., 2021). The algorithm works as follows: Given a list of tactics L
with priority, we maintain a priority queue Q of tactic states whose
priority is given by the priority of the last applied tactic in L that
led to it. While Q is not empty, we pop the top tactic state t from Q.
We iterate through L and apply each tactic to t. If no error is raised,
we capture the returned tactic states from Lean and insert them back
into Q.

We use the same terminology as in PACT (Han et al., 2021): maximum queue
size \(\omega_{max}\) , depth limit \(d_{max}\) . We also enforce a
budget of \(i_{max}\) iterations of the outer loop. When Q's size
reaches \(q_{max}\) , all the tactic states to be inserted are
discarded. We do not expand the next tactic state when the depth is
beyond \(d_{max}\) . This loop is run until a proof is found or the
iterations budget is exhausted.

For consistency checking, we run the tidy baseline under the same
settings and on the same test set as in PACT (Han et al., 2021) except
that we don't set a global timeout. Our implementation

achieved a 10.5\% pass rate on mathlib's test split. This result is
comparable to the reported 9.9\% in PACT given the waived global
timeout.

In addition to the curated list of tactics L used in PACT (Han et al.,
2021), we added 4 high-level tactics
\(HL = [nlinarith, linarith, ring_nf, norm_num]\) to L with higher
priorities than the others. We report our pass rate on miniF2F in Table
2.

Table 2: The table shows the number of solved statement in miniF2F when
running the tidy baseline with different values of \(i_{max}\) as well.
Lean's built-in tidy tactic. All tidy baseline experiments are run with
\(\omega_{max} = 128\) , \(d_{max} = 8\) using \(L + HL\) . Despite the
tidy baseline being deterministic, it is still subject to per-tactic
application timeouts, explaining the number 43 reported on miniF2F-test
for \(i_{max} = 32\) .

parameters

miniF2F-valid

miniF2F-test

Lean\textquotesingle s tidy tactic

12 / 244

13 / 244

\(i_{max} = 1\)

21 / 244

23 / 244

\(i_{max} = 2\)

31 / 244

29 / 244

\(i_{max} = 4\)

38 / 244

41 / 244

\(i_{max} = 8\)

41 / 244

44 / 244

\(i_{max} = 16\)

41 / 244

44 / 244

\(i_{max} = 32\)

41 / 244

43 / 244

\(i_{max} = 64\)

41 / 244

44 / 244

\(i_{max} = 128\)

41 / 244

44 / 244

\section{4.2.2 GPT-F/PACT}\label{gpt-fpact}

We report the pass rate of GPT-f/PACT as described in Han et al.~(2021).
We use a model with 700M learnable parameters. The model is trained on
an updated dump \(^{56}\) of the mathlib library using the PACT
methodology denoted in the paper as mix2 \textgreater{} mix1 + tactic in
Figure 6.

The model achieves a Pass@1 of 24.6\% and a Pass@8 of 29.2\% on
miniF2F-test. The average proof length is also reported in Table 3.

Table 3: Baseline performance on Metamath and Lean. All proof searches
are provided with a 128 expansions budget. GPT-f attempts e = 16 tactics
per expansion while the tidy baseline attempts e = 17 tactics per
expansion (L + HL, see section 4.2.1). Reported proof lengths are
averages over all the proofs found in each run. Note that the tidy
baseline being deterministic, there is no point attempting a proof
search more than once.

miniF2F-valid

miniF2F-test

Formal System

Model

Proof Length

Pass rate Pass@1

Pass@8

Proof Length

Pass rate Pass@1

Pass@8

Metamath

GPT-f

16.2

1.0\%

2.0\%

20.3

1.3\%

1.6\%

Lean

tidy

1.7

16.8\%

-

1.8

18.0\%

-

Lean

GPT-f

2.6

23.9\%

29.3\%

2.5

24.6\%

29.2\%

\section{4.3 DISCUSSION}\label{discussion}

\section{4.3.1 ACCESS TO HIGH-LEVEL
TACTICS}\label{access-to-high-level-tactics}

One goal of miniF2F is to study the comparison of performance across
formal systems. In this section we reported the performance of the same
methodology (GPT-f (Polu \& Sutskever, 2020))

applied to both Lean and Metamath. Both models are pre-trained on
WebMath (Polu \& Sutskever, 2020) and respectively trained on datasets
extracted from Lean (Han et al., 2021) and Metamath (Polu \& Sutskever,
2020). The overall compute deployed at training is comparable in both
setup and exactly equivalent at test-time, yet the achieved performance
appears drastically superior when applied to Lean. We hypothesize that
this is mainly explained by the model's access to high-level tactics
when applied to Lean, enabling the model to learn how to guide Lean's
automation in an effective way.

An example of this high-level guidance behavior is well exemplified by
the following proof of the statement algebra\_sqineq\_2unitcircatblt1
where the model heavily relies on Lean's nlinarith solver but provides
it with essential premises to successfully guide the search.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{theorem algebra\_sqineq\_2unitcircatblt1}
\NormalTok{(a b : R)}
\NormalTok{(h0 : a\^{}2 + b\^{}2 = 2) :}
\NormalTok{a * b ≤ 1 :=}
\NormalTok{begin}
\NormalTok{nlinarith [sq\_nonneg a, sq\_nonneg b, sq\_nonneg (a {-} b)]}
\NormalTok{end }
\end{Highlighting}
\end{Shaded}

(The statement above (algebra\_sqineq\_2unitcircatblt1) requires to
prove the assertion
\(\forall a, b \in \mathbb{R}, a^2 + b^2 = 2 \to a \cdot b \leq 1\) ).

In Metamath, GPT-f fails to find a proof as it requires a very large
number of steps to appropriately rewrite the goal in a way that is
amenable to the use of set.mm's existing theorems. The tidy baseline
also fails to find a proof of that statement as nlinarith is not capable
of solving the goal without being passed extraneous premises.

These results motivate the use of neural theorem proving with formal
systems that expose powerful high level tactics and also suggest the
potential of a closer collaboration between formal systems and machine
learning practitioners. It also motivates the use of generative models
in that setup as the arguments required by high-level tactics to succeed
on non trivial problems generally do not exist in the context of the
statement and therefore have to be generated ex-nihilo.

\section{4.3.2 COMPARISON OF INFORMAL AND FORMAL
SETUPS}\label{comparison-of-informal-and-formal-setups}

The use of formal systems for neural theorem proving is often motivated
by the role of the formal system as a verifier, enabling more advanced
neural search strategies than possible in a fully informal setup where
the generation of a model can't be verified automatically, as well as
the access to powerful tactics. Our formalization of a subset of the
MATH (Hendrycks et al., 2021) informal dataset provides an interesting
approximate quantification of the benefit of having access to a formal
system in the context of neural theorem proving. Approximate, because we
only formalized a small subset of the MATH statements, but nonetheless
useful since we drew uniformly from the 5 difficulty levels.

In Hendrycks et al.~(2021), the performance of GPT-3 (which is a larger
model than the GPT-f model studied here) is reported to be 6.0\% in the
algebra category and 3.9\% in the number theory category. GPT-f applied
to Lean by comparison achieves 51.4\% in the algebra category and 41.7\%
in the number theory category. It is also worthwhile to note that the
tidy baseline also highly outperforms (31.4\% in algebra and 30.0\% in
number theory) GPT-3 in an informal setup demonstrating the benefit of
proof automation alone.

\section{4.3.3 LIMITATION}\label{limitation}

With miniF2F being cross-system as the goal, types of problems that are
less expressible in certain systems such as geometry and combinatorial
problems are less covered. The shift of distribution of problem types
may result in skewing the research direction of models when benchmarking
on miniF2F. Directionally we aim to fix it and extend the coverage of
miniF2F as we grow the benchmark. However, works and efforts on the
corresponding library of other systems are required as well.

\section{5 CONCLUSION}\label{conclusion}

We presented miniF2F, a dataset of formal Olympiad-level mathematics
problem statements, meant to serve as an initial effort towards
cross-system benchmarking of neural mathematical reasoning capabilities
in formal environments. We reported the performance of the neural
theorem prover GPT-f (Polu \& Sutskever, 2020) on both the Lean and
Metamath parts of miniF2F as well as the performance of our non-neural
tidy baseline applied to Lean. Then, we discussed these baselines and
put them in perspective with previously reported comparable results in
informal environments (Hendrycks et al., 2021).

Finally, we hope that miniF2F will prove to be useful to the scientific
community working on neural theorem proving and spur advances in this
domain.

\section{ACKNOWLEDGMENTS}\label{acknowledgments}

We are grateful to Wenda Li and Xavier Martinet for contributing the
Isabelle and HOL Light statements currently available in miniF2F, paving
the way towards a full support of Isabelle and HOL Light, as well as
their feedback and encouragement in the process. We thank Harri Edwards
for his comments that greatly improved the manuscript.

\section{REFERENCES}\label{references}

Kshitij Bansal, Sarah Loos, Markus Rabe, Christian Szegedy, and Stewart
Wilcox. Holist: An environment for machine learning of higher order
logic theorem proving. In International Conference on Machine Learning,
pp.~454--463. PMLR, 2019a.\\
Kshitij Bansal, Christian Szegedy, Markus N Rabe, Sarah M Loos, and
Viktor Toman. Learning to reason in large theories without imitation.
arXiv preprint arXiv:1905.10501, 2019b.\\
Tom Brown, Benjamin Mann, Nick Ryder, Melanie Subbiah, Jared D Kaplan,
Prafulla Dhariwal, Arvind Neelakantan, Pranav Shyam, Girish Sastry,
Amanda Askell, Sandhini Agarwal, Ariel Herbert-Voss, Gretchen Krueger,
Tom Henighan, Rewon Child, Aditya Ramesh, Daniel Ziegler, Jeffrey Wu,
Clemens Winter, Chris Hesse, Mark Chen, Eric Sigler, Mateusz Litwin,
Scott Gray, Benjamin Chess, Jack Clark, Christopher Berner, Sam
McCandlish, Alec Radford, Ilya Sutskever, and Dario Amodei. Language
models are few-shot learners. In H. Larochelle, M. Ranzato, R. Hadsell,
M. F. Balcan, and H. Lin (eds.), Advances in Neural Information
Processing Systems, volume 33, pp.~1877--1901. Curran Associates, Inc.,
2020. URL
https://proceedings.neurips.cc/paper/2020/file/1457c0d6bfcb4967418bfb8ac142f64a-Paper.pdf.\\
Kevin Buzzard, Johan Commelin, and Patrick Massot. Lean perfectoid
spaces. https://leanprover-community.github.io/lean-perfectoid-spaces/,
2019.\\
Jia Deng, Wei Dong, Richard Socher, Li-Jia Li, Kai Li, and Li Fei-Fei.
Imagenet: A large-scale hierarchical image database. In 2009 IEEE
conference on computer vision and pattern recognition, pp.~248--255.
Ieee, 2009.\\
Jesse Michael Han, Jason Rute, Yuhuai Wu, Edward W Ayers, and Stanislas
Polu. Proof artifact co-training for theorem proving with language
models. arXiv preprint arXiv:2102.06203, 2021.\\
Maximilian P. L. Haslbeck, Tobias Nipkow, and Simon Wimmer. Proof
ground. https://www21.in.tum.de/\textasciitilde wimmers/proofground/,
2019.\\
Dan Hendrycks, Collin Burns, Saurav Kadavath, Akul Arora, Steven Basart,
Eric Tang, Dawn Song, and Jacob Steinhardt. Measuring mathematical
problem solving with the math dataset. arXiv preprint arXiv:2103.03874,
2021.\\
The mathlib Community. The lean mathematical library. In Jasmin
Blanchette and Catalin Hritcu (eds.), Proceedings of the 9th ACM SIGPLAN
International Conference on Certified Programs and Proofs, CPP 2020, New
Orleans, LA, USA, January 20-21, 2020, pp.~367--381. ACM, 2020. doi:
10.1145/3372885.3373824. URL https://doi.org/10.1145/3372885.3373824.

Aditya Paliwal, Sarah Loos, Markus Rabe, Kshitij Bansal, and Christian
Szegedy. Graph representations for higher-order logic and theorem
proving. In Proceedings of the AAAI Conference on Artificial
Intelligence, volume 34, pp.~2967--2974, 2020.\\
Denis Paperno, Germán Kruszewski, Angeliki Lazaridou, Quan Ngoc Pham,
Raffaella Bernardi, Sandro Pezzelle, Marco Baroni, Gemma Boleda, and
Raquel Fernández. The LAMBADA dataset: Word prediction requiring a broad
discourse context. In Proceedings of the 54th Annual Meeting of the
Association for Computational Linguistics, ACL 2016, August 7-12, 2016,
Berlin, Germany, Volume 1: Long Papers. The Association for Computer
Linguistics, 2016. doi: 10.18653/v1/p16-1144. URL
https://doi.org/10.18653/v1/p16-1144.\\
Stanislas Polu and Ilya Sutskever. Generative language modeling for
automated theorem proving. arXiv preprint arXiv:2009.03393, 2020.\\
Pranav Rajpurkar, Jian Zhang, Konstantin Lopyrev, and Percy Liang.
Squad: 100, 000+ questions for machine comprehension of text. In Jian
Su, Xavier Carreras, and Kevin Duh (eds.), Proceedings of the 2016
Conference on Empirical Methods in Natural Language Processing, EMNLP
2016, Austin, Texas, USA, November 1-4, 2016, pp.~2383--2392. The
Association for Computational Linguistics, 2016. doi:
10.18653/v1/d16-1264. URL https://doi.org/10.18653/v1/d16-1264.\\
David Saxton, Edward Grefenstette, Felix Hill, and Pushmeet Kohli.
Analysing mathematical reasoning abilities of neural models. In 7th
International Conference on Learning Representations, ICLR 2019, New
Orleans, LA, USA, May 6-9, 2019. OpenReview.net, 2019. URL
https://openreview.net/forum?id=H1gR5iR5FX.\\
Peter Scholze. Liquid tensor experiment.
https://xenaproject.wordpress.com/2020/12/05/liquid-tensor-experiment/,
2020.\\
Daniel Selsam, Kevin Buzzard, Reid Barton, Percey Liang, Sarah Loss, and
Freek Wiedijk. Imo grand challenge.
https://imo-grand-challenge.github.io/, 2019.\\
G. Sutcliffe. The CADE ATP System Competition - CASC. AI Magazine,
37(2):99--101, 2016.\\
G. Sutcliffe. The TPTP Problem Library and Associated Infrastructure.
From CNF to TH0, TPTP v6.4.0. Journal of Automated Reasoning,
59(4):483--502, 2017.\\
Alex Wang, Amanpreet Singh, Julian Michael, Felix Hill, Omer Levy, and
Samuel R. Bowman. GLUE: A multi-task benchmark and analysis platform for
natural language understanding. In 7th International Conference on
Learning Representations, ICLR 2019, New Orleans, LA, USA, May 6-9,
2019. OpenReview.net, 2019. URL
https://openreview.net/forum?id=rJ4km2R5t7.\\
Sean Welleck, Jiacheng Liu, Ronan Le Bras, Hannaneh Hajishirzi, Yejin
Choi, and Kyunghyun Cho. Naturalproofs: Mathematical theorem proving in
natural language. arXiv preprint arXiv:2104.01112, 2021.\\
Daniel Whalen. Holophrasm: a neural automated theorem prover for
higher-order logic. CoRR, abs/1608.02644, 2016. URL
http://arxiv.org/abs/1608.02644.\\
Freek Wiedijk. Formalizing 100 theorems.
https://www.cs.ru.nl/\textasciitilde freek/100/, 2008.\\
Yuhuai Wu, Albert Jiang, Jimmy Ba, and Roger Baker Grosse. INT: an
inequality benchmark for evaluating generalization in theorem proving.
In 9th International Conference on Learning Representations, ICLR 2021,
Virtual Event, Austria, May 3-7, 2021. OpenReview.net, 2021. URL
https://openreview.net/forum?id=O6LPudowNQm.\\
Kaiyu Yang and Jia Deng. Learning to prove theorems via interacting with
proof assistants. In International Conference on Machine Learning,
pp.~6984--6994. PMLR, 2019.

\section{A EXAMPLE OF STATEMENT IN
MINIF2F}\label{a-example-of-statement-in-minif2f}

Table 4: Problem 11 of 2000 AMC 12 is formalized with proof in different
languages in miniF2F. The proof is optionally attached thus not part of
the benchmark. The proof in Metamath is too long to be fully displayed.

Natural Language

Two non-zero real numbers, a and b, satisfy ab = a - b. Which of the
following is a possible value of a/b + b/a - ab? (A) -2 (B) -1/2 (C) 1/3
(D) 1/2 (E) 2

Metamath

\$\{ amc12-2000-p11.0 \$e \textbar{} - ( ph -\textgreater{} A e. RR )
\$. amc12-2000-p11.1 \$e \textbar{} - ( ph -\textgreater{} B e. RR ) \$.
amc12-2000-p11.2 \$e \textbar{} - ( ph -\textgreater{} A =/= 0 ) \$.
amc12-2000-p11.3 \$e \textbar{} - ( ph -\textgreater{} B =/= 0 ) \$.
amc12-2000-p11.4 \$e \textbar{} - ( ph -\textgreater{} ( A x. B ) = ( A
- B ) ) \$. amc12-2000-p11 \$p \textbar{} - ( ph -\textgreater{} ( ( ( A
/ B ) + ( B / A ) ) - ( A x. B ) ) = 2 ) \$= ( cdiv co caddc cmul cmin
c2 cexp eqcomd \ldots{} \$. \$\}

Lean

theorem amc12\_2000\_p11 (a b : R) (h0 : a ≠ 0 ∧ b ≠ 0) (h1 : a * b = a
- b) : a / b + b / a - a * b = 2 := begin field\_simp {[}h0.1, h0.2{]},
simp only {[}h1, mul\_comm, mul\_sub{]}, ring, end

Isabelle

theorem amc12\_2000\_p11: fixes a b::real assumes "a
\&lt;noteq\textgreater{} 0" "b \&lt;noteq\textgreater{} 0" and "a * b =
a - b" shows "a / b + b / a - a * b = 2" using assms by (smt (verit,
ccfv\_threshold) diff\_divide\_distrib div\_self
divide\_divide\_times\_eq eq\_divide\_imp
nonzero\_mult\_div\_cancel\_left) end

\section{B PERFORMANCE BY DIFFICULTY ON STATEMENTS FORMALIZED FROM MATH
DATASET}\label{b-performance-by-difficulty-on-statements-formalized-from-math-dataset}

The MATH dataset assigns a difficulty ranging from 1 to 5 to each of its
problem. Tables 5 and 6 report the number of proved statement split by
difficulty level on the algebra and number theory categories.

Table 5: Counts of successfully proved statements formalized from
MATH-Algebra in miniF2F v1 split by difficulty. This table corresponds
to ``MATH Algebra'' in Figure 1.

Difficulty Level

miniF2F-valid

miniF2F-test

1

2

3

4

5

1

2

3

4

5

Metamath/GPT-f

1

0

0

0

0

2

0

1

0

1

Lean/tidy

6

4

2

2

1

6

4

7

3

1

Lean/GPT-f

9

7

8

6

2

8

7

10

7

3

Table 6: Counts of successfully proved statements formalized from
MATH-Number theory in miniF2F v1 split by difficulty. This table
corresponds to ``MATH Number Theory'' in Figure 1.

Difficulty Level

miniF2F-valid

miniF2F-test

1

2

3

4

5

1

2

3

4

5

Metamath/GPT-f

0

0

0

0

0

0

0

0

0

0

Lean/tidy

8

3

2

2

2

7

4

3

2

2

Lean/GPT-f

9

5

5

4

2

10

5

5

3

2

More broadly, Lean GPT-f is capable of solving any problem that the tidy
baseline or Metamath GPT-f can solve in MiniF2F. Qualitatively, the
problems on which it fail either require multiple non-trivial reasoning
steps (outside a few exceptions, problems requiring more than 2
non-trivial steps of mathematical reasoning are generally out of reach
of these baselines) or require a cut introduction that is hard to
generate, such as generating a non trivial witness.

\end{document}
