\documentclass{article}
\usepackage{xcolor}
\newcommand{\myhighlight}[1]{\textcolor{blue}{#1}}

% The draft follows the supplied NeurIPS-style template when the local style
% file exists, and falls back to a standard preprint layout in this workspace.
\IfFileExists{neurips_2026.sty}{%
  \usepackage{neurips_2026}
}{%
  \usepackage[margin=1in]{geometry}
  \usepackage[numbers,sort&compress]{natbib}
  
}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{hyperref}
\usepackage{url}
\usepackage{booktabs}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{nicefrac}
\usepackage{microtype}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{tabularx}
\usepackage{array}
\usepackage{graphicx}
\usepackage{tikz}
\usetikzlibrary{arrows.meta, positioning, patterns}

\usepackage{mathtools}
\usepackage{amsthm}
\theoremstyle{plain}
% \newtheorem{findings}{Findings}
\newtheorem{desideratum}{Desideratum}
\renewcommand{\thedesideratum}{\Roman{desideratum}}



\hypersetup{
  colorlinks=true,
  linkcolor=blue,
  citecolor=blue,
  urlcolor=blue
}

\title{{\textit{Shared Your Tokens!}  A Protocol for Leveraging Local Tokens  for  Distributed ``Intelligent'' Tasks}}
\author{Hongzhan Tu}
\author{Zhizhou Wang}

\begin{document}

\maketitle

\begin{abstract}
{\color{blue}
Large intelligent tasks increasingly require more than a single generation step: they require decomposition, bounded execution, domain-specific verification, canonical output selection, merge, contribution accounting, and replayable audit evidence. This paper presents TokenShare, a local research prototype that treats those concerns as protocol objects rather than orchestration folklore. TokenShare represents a root task as a recursively expandable task DAG, records requests, submissions, artifacts, verification reports, canonical bindings, merge records, contribution records, and sandbox settlement facts in an append-only event ledger, and rebuilds materialized state from JSONL, SQLite, and content-addressed artifacts.

The prototype separates a task-independent protocol kernel from task plugins and executors. We instantiate the design with two real proof-of-concept plugins: integer factorization with deterministic range verification and a Lean formal-proof plugin backed by a fixed local Lean/lake environment, checker logs, proof artifacts, and environment manifests. We also evaluate an experiment-scoped AI API executor that persists raw model outputs, parsed outputs, parser failures, usage, cost, latency, and provider provenance without giving the executor authority over task semantics. Across 17 default experiment runs, TokenShare exercises end-to-end factorization, failure injection, mechanism ablation, and cross-plugin generality, producing 1215 events and 510 artifacts. The results support the paper's central claim: useful intelligent work can be studied as a replayable protocol lifecycle in which decomposition, verification, merge, and accounting remain explicit, typed, and auditable.
}
\end{abstract}

\section{Introduction}

{\color{blue}
Modern AI work is increasingly mediated by scarce execution resources: model tokens, tool calls, local compute, formal checkers, human attention, and time-bounded repair attempts. The core systems question is no longer whether a single model call can emit an answer, but whether a larger unit of useful work can be decomposed, assigned, verified, merged, and audited without losing the evidence that justifies the final artifact.

Meaningful workloads often cross the boundary of a prompt-response interaction. Scientific computation, formal reasoning, benchmark construction, data transformation, and annotation all require structured intermediate states, explicit acceptance criteria, and accountable integration. When a task is modular and verification-heavy, its value depends on the lifecycle around candidate outputs: what was requested, what was executed, what evidence was produced, which checker accepted it, how canonical state was chosen, how child results were merged, and how the final contribution record can be replayed.

TokenShare addresses this setting as a protocol-kernel problem. A root task is represented as a typed task unit; plugin-owned split strategies may expand verified canonical outputs into child units and merge plans; executors only produce submissions and artifacts; verification and canonical selection are recorded as protocol facts; and every state-changing decision is written to an append-only ledger. The resulting system turns fragmented execution capacity into auditable, mergeable, and replayable work while preserving a clean boundary between protocol mechanics and task semantics.
}

This paper makes three main \textbf{contributions}:

\begin{itemize}
\item \textcolor{blue}{We formulate decomposable intelligent work as a replayable protocol lifecycle with typed artifacts, event-sourced state, and plugin-owned task semantics.}
 \item \textcolor{blue}{We design and implement TokenShare, a local protocol kernel that supports registry snapshots, leases, execution requests and submissions, verification reports, canonical output binding, expansion, merge, contribution accounting, sandbox settlement, and artifact-backed audit evidence.}
\item  \textcolor{blue}{We evaluate the design with real factorization and Lean proof plugins, failure injection, mechanism ablation, cross-plugin generality, and an experiment-scoped AI API executor that preserves raw-output provenance while keeping parsing and verification under plugin control.}
\end{itemize}






\section{\textcolor{blue}{Motivation Towards Replayable Intelligent Work}}


\subsection{Background}

\textbf{\textcolor{blue}{Metered Units of Intelligent Work}}~
{\color{blue}
Model tokens are only one visible unit of modern intelligent work. In practice, a useful result may also consume local compute, tool calls, checker invocations, structured parsing, repair attempts, and human or programmatic review. We therefore use ``token'' in the broad systems sense of a metered execution contribution: an attempt spends some bounded resource and produces an artifact that must be checked before it can influence the accepted state.
}

\textbf{\textcolor{blue}{The Price of Evidence}}~
{\color{blue}
The price of such work is not captured by final-answer correctness alone. A single correct answer says little about which intermediate outputs were rejected, whether the same state can be reconstructed, whether a checker was run in a fixed environment, or whether a merge consumed exactly the verified child outputs it claims. TokenShare treats this hidden cost as protocol data: inputs, requests, submissions, raw outputs, parsed outputs, checker evidence, canonical choices, merge records, and contribution records are persisted explicitly.
}


\subsection{Motivations}

{\color{blue}
The motivating question is therefore: \emph{Can useful intelligent work be represented as a small set of reusable protocol transitions, while leaving domain-specific semantics to plugins and executor-specific behavior to executor adapters?}

TokenShare answers this question with an event-sourced local protocol prototype. The protocol core maintains task units, dependency edges, leases, attempts, artifact references, verification reports, canonical output bindings, expansion decisions, merge records, contribution records, and settlement records. A task plugin defines schemas, split strategies, validators, parsers, and merge policies. An executor receives a structured request and returns a structured submission with artifact references. The core coordinates the lifecycle, but it does not infer factorization mathematics, Lean proof semantics, or model-output schemas.

This architecture is intentionally useful for research: it makes mechanism boundaries visible. When an output is malformed, the parser boundary should catch it. When an output is structured but wrong, the plugin verifier should reject it. When a partial child set is insufficient, the merge gate should block parent completion. When a model call is made, raw and parsed artifacts, usage, cost, and provider provenance should remain audit-visible without allowing the executor to decide correctness.
}

\section{The Design Philosophy}
\subsection{Problem Formulation}

{\color{blue}
We consider a root task $T$ whose accepted output may require intermediate claims, checker evidence, and merge steps. TokenShare models the task as an event-sourced protocol instance:
\[
\mathcal{P}_T=(G_T,\mathcal{A}_T,\mathcal{E}_T,\mathcal{R}_T),
\]
where $G_T$ is a typed task DAG, $\mathcal{A}_T$ is a content-addressed artifact set, $\mathcal{E}_T$ is an append-only event log, and $\mathcal{R}_T$ is a frozen registry snapshot for the plugin and executor descriptors used by the run.

A task unit $u$ is not merely a function call. It is a protocol object
\[
u=(\mathrm{spec}_u,\mathrm{state}_u,\mathrm{inputs}_u,\mathrm{expected}_u,\mathrm{plugin}_u,\mathrm{deps}_u),
\]
and an execution attempt $a$ is separately tracked through a lease, request, submission, verification report, and possible canonical binding. This separation is central: lease validity, attempt progress, task completion, and contribution accounting are distinct state lines rather than one overloaded status field.

Recursive decomposition is also explicit. A plugin-owned split strategy may transform an already verified canonical output bundle into
\[
\mathrm{Split}_p(u,\hat{Y}_u)\rightarrow(\Delta G, \mathrm{MergePlan}),
\]
where $\Delta G$ contains child units and dependencies, and the merge plan records the required child output slots. The protocol kernel records and validates this proposal, but the domain logic that decides the shape of $\Delta G$ belongs to the plugin.
}



\subsection{Desiderata of TokenShare Protocol}


\begin{desideratum}
\textbf{Decomposability:}~ A TokenShare task should be expressible as a structured task tree or directed acyclic graph whose executable units have clear inputs, outputs, dependencies, and merge relations.
\end{desideratum}

{\color{blue}
A TokenShare task must be decomposable into typed units whose inputs, expected outputs, dependencies, and merge slots can be persisted and replayed. Decomposition is not a free-form plan emitted by an executor; it is a versioned plugin decision recorded through a structured proposal and an expansion event batch. In the factorization plugin, decomposition partitions a candidate divisor domain into bounded range units. In the Lean plugin, decomposition is produced by a deterministic Lean-side helper that emits a split certificate and a merge skeleton. In both cases, the protocol core only checks the common lifecycle contract.
}


\begin{desideratum}
\textbf{Local Verifiability:}~ \textcolor{blue}{Each executable subtask should include an explicit verifier that can check whether its submitted output is valid before that output is accepted, merged, or counted as eligible contribution evidence.}
\end{desideratum}

{\color{blue}
Each candidate output must be verifiable before it is eligible for canonical state. TokenShare separates parsing, structural checks, domain verification, and canonical selection. For factorization, the plugin verifier rechecks whether a claimed factor divides the target and whether a no-factor range claim is consistent with its bounded domain. For Lean proof production, the validator accepts only checker reports backed by a fixed local Lean/lake environment, generated source, stdout/stderr logs, proof artifacts, and an environment reference. A raw model response or executor submission is therefore evidence, not authority.
}


\begin{desideratum}
\textbf{Extendability:}~ The protocol should provide a reusable coordination skeleton while allowing each task family to plug in task-specific schemas, verifiers, merge rules, cost models, and contributor requirements.
\end{desideratum}

{\color{blue}
The protocol should be reusable without absorbing task semantics. TokenShare implements this through frozen plugin descriptors and executor descriptors. A plugin supplies task types, schemas, parser policy, split strategy, validator policy, and merge policy. An executor supplies a transport or local execution boundary and returns artifacts. This makes the same protocol kernel coordinate arithmetic range search and Lean proof checking while keeping divisibility rules and proof-checking rules outside the kernel.
}


\begin{desideratum}
\textbf{Scalability:}~ As more tokens, agents, workers, or computational resources become available, the protocol should convert that additional capacity into faster completion, higher quality, broader verification, or stronger fault tolerance.
\end{desideratum}

{\color{blue}
The relevant scaling unit is not only the number of workers, but the amount of independently checkable evidence the protocol can admit without corrupting canonical state. TokenShare therefore scales through smaller typed artifacts, explicit lease and attempt records, deterministic merge gates, and replayable event batches. Additional execution capacity is useful only when its output can be parsed, verified, linked to an expected slot, and merged under a recorded policy.
}


\begin{desideratum}
\textbf{Autonomy:}~ The protocol should advance tasks through assignment, execution, validation, verification, merging, timeout recovery, reassignment, and settlement according to predefined rules with minimal continuous manual coordination.
\end{desideratum}

{\color{blue}
The protocol should advance routine lifecycle transitions from recorded facts rather than conversational memory. A request produces a submission; a submission produces a verification report; verified candidates may compete for a single canonical output bundle; canonical outputs may trigger completion or expansion; merge records and expected-output resolution produce parent completion; eligible canonical contributions enter a sandbox settlement batch. The autonomy claim is therefore operational: the system can inspect its ledger and artifacts to explain why a task progressed, blocked, or rejected an output.
}



\section{The TokenShare Protocol}

{\color{blue}
TokenShare is a protocol kernel for useful work whose intermediate states must be explainable after the fact. The kernel has three boundaries: protocol objects and state transitions, task plugins, and executors. Protocol objects define the reusable lifecycle; plugins define task semantics; executors produce submissions under a request contract. The event ledger and artifact store connect the three layers by making every authority-bearing fact persistent.
}

\subsection{Overall Picture}

{\color{blue}
Figure~\ref{fig:tokenshare-overall} shows the implemented architecture. A root task enters the protocol through a typed \texttt{TaskSpec} and input artifact. The protocol engine records registry snapshots, schedules ready units through leases, records execution requests and submissions, invokes verification and canonical selection, accepts plugin-owned expansion proposals, resolves merge tasks, creates contribution records, and writes sandbox settlement records. SQLite is a materialized index over the append-only event ledger rather than the source of authority.
}

\begin{figure}[htbp]
\centering
\resizebox{\linewidth}{!}{
\begin{tikzpicture}[
    node distance=0.9cm and 1.0cm,
    box/.style={
        rectangle,
        rounded corners,
        draw=blue!70!black,
        fill=blue!5,
        thick,
        align=center,
        minimum width=3.25cm,
        minimum height=0.95cm,
        font=\small,
        text=blue!45!black
    },
    wide/.style={
        rectangle,
        rounded corners,
        draw=blue!70!black,
        fill=blue!8,
        thick,
        align=center,
        minimum width=7.1cm,
        minimum height=0.85cm,
        font=\small,
        text=blue!45!black
    },
    arrow/.style={-{Latex[length=2.5mm]}, thick, draw=blue!70!black},
    dashedarrow/.style={-{Latex[length=2.5mm]}, thick, dashed, draw=blue!70!black}
]

\node[box] (input) {Root task\\\texttt{TaskSpec} + input artifact};
\node[box, right=of input] (engine) {ProtocolEngine\\lifecycle transitions};
\node[box, right=of engine] (graph) {TaskGraph\\units + dependencies};

\node[box, below=of engine] (registry) {Frozen registries\\plugins + executors};
\node[box, below=of input] (plugins) {Task plugins\\schemas, split, verify, merge};
\node[box, below=of graph] (executors) {Executors\\request $\rightarrow$ submission};

\node[wide, below=1.15cm of registry] (ledger) {Append-only JSONL EventLedger\\state changes, verification reports, canonical bindings, expansion, merge, contribution, settlement};
\node[wide, below=of ledger] (store) {ArtifactStore + SQLite projection\\content-addressed evidence and rebuildable indexes};

\draw[arrow] (input) -- (engine);
\draw[arrow] (engine) -- (graph);
\draw[arrow] (engine) -- (registry);
\draw[arrow] (registry) -- (plugins);
\draw[arrow] (registry) -- (executors);
\draw[arrow] (plugins) -- (engine);
\draw[arrow] (executors) -- (engine);
\draw[dashedarrow] (engine) -- (ledger);
\draw[dashedarrow] (plugins) -- (ledger);
\draw[dashedarrow] (executors) -- (ledger);
\draw[arrow] (ledger) -- (store);

\end{tikzpicture}
}
\caption{\textcolor{blue}{Overall architecture of the TokenShare protocol. The protocol core owns lifecycle transitions and event recording; task plugins own domain schemas, split strategies, validators, parsers, and merge policies; executors own bounded execution and artifact-producing submissions.}}
\label{fig:tokenshare-overall}
\end{figure}

\subsection{Task Registration, Decomposition, Assignment, and Commitment}

\subsubsection{Task Registration}

{\color{blue}
A registered task is a typed protocol object rather than an informal request. The root \texttt{TaskUnit} stores a \texttt{TaskSpec}, plugin identity, required outputs, dependency state, and artifact references. The input body is persisted through a content-addressed artifact reference, and task creation is recorded as an event. This gives later verification and replay a stable object identity:
\[
\mathrm{Root}(T)=
(\mathrm{task\_id},\mathrm{unit\_id},\mathrm{plugin\_id},\mathrm{input\_ref},\mathrm{required\_outputs}).
\]
}

\subsubsection{Recursive Task Decomposition}

{\color{blue}
TokenShare expands only from accepted evidence. A candidate output first passes parser and plugin-domain validation. If it is selected as the canonical output bundle for a unit, the plugin split strategy may derive a \texttt{DecompositionProposal} and a \texttt{MergePlan}. The accepted expansion is committed as a batch:
\[
\mathrm{proposal}\; \rightarrow\; \mathrm{decision}\; \rightarrow\; \mathrm{merge\ plan}\; \rightarrow\; \mathrm{child\ units}\; \rightarrow\; \mathrm{TASK\_EXPANDED}.
\]
This order prevents child tasks from appearing as authoritative state before the proposal, decision, and merge requirements that justify them.
}

\subsubsection{Task Assignment and Commitment}

{\color{blue}
Assignment is represented by leases and attempts. A scheduler selects ready units under a protocol configuration, a \texttt{LeaseManager} records an active lease with a fencing token, and an execution request binds an attempt to the task, unit, lease, executor descriptor, input artifacts, and optional prompt package. A submission advances an attempt only when it matches the current task, unit, attempt, lease, and fencing token. This gives TokenShare the commitment property it needs for auditability: an executor cannot retroactively make a submission authoritative for a different leased unit.
}

\subsection{Execution, Verification, Recursive Merge, and Settlement}

\subsubsection{Client-Side Execution and Local Validation}

{\color{blue}
Executors operate behind a uniform request/submission interface. A deterministic local executor may compute a bounded factor-search result; the AI API executor may call a model and persist raw provider output; the Lean checker path may generate checker reports and proof artifacts. In every case, the executor returns artifact references and provenance, not protocol acceptance. Local validation is useful as an executor-side guardrail, but accepted protocol state begins only after the recorded submission is parsed, verified, and selected through the protocol lifecycle.
}

\subsubsection{Server-Side Verification}

{\color{blue}
Server-side verification is layered. The protocol checks artifact presence, schema shape, required-output coverage, and attempt linkage. The plugin then performs domain validation. Factorization verifies range outputs by deterministic arithmetic recheck. Lean validation requires a real checker report with generated source, proof artifact, stdout/stderr logs, and an \texttt{EnvironmentRef}. Verification produces an auditable report; canonical selection is a separate event that binds one eligible output bundle for a task unit.
}

\subsubsection{Recursive Result Merging}

{\color{blue}
Merge is represented as another protocol task rather than an implicit post-processing step. A \texttt{MergePlan} records required slots, expected child output refs, schema requirements, and the plugin merge policy. A merge task becomes resolvable only when all required slots have canonical child outputs. The plugin merge policy constructs the candidate parent output, the protocol records a \texttt{MergeRecord}, and expected-output resolution determines whether the parent can complete or must remain unresolved.
}

\subsubsection{\textcolor{blue}{Protocol Settlement}}

{\color{blue}
TokenShare's current accounting layer is protocol-internal and evidence-derived. Contributions are derived from canonical completion, accepted expansion, and accepted merge facts. A root-level settlement batch consumes the complete eligible contribution set, writes a \texttt{SettlementRecord}, persists settlement entries as an artifact, and advances the corresponding contribution records to settled. The useful invariant is idempotence: a completed root can be accounted for once from the same event and artifact evidence, and replay can inspect the batch without re-executing the task.
}




\section{A Robust Fault-Tolerance Mechanism}

{\color{blue}
Fault tolerance in TokenShare is expressed as evidence isolation. A failed executor call, malformed model response, invalid domain output, expired lease, or incomplete merge should leave an auditable trace without contaminating canonical state. The current prototype evaluates this principle through parser isolation, deterministic plugin verification, lease expiry and requeue, bounded verifier budgets, all-required merge gates, and idempotent settlement batches.
}

\subsection{Failure Model}

{\color{blue}
The experiment suite distinguishes five implemented failure classes:
\begin{itemize}
\item \textbf{Offline}: an assigned unit stops producing valid submissions and must be recovered through the lease path.
\item \textbf{Slow}: progress is delayed relative to the lease and scheduling configuration.
\item \textbf{Executor error}: the execution boundary records a failed call rather than a candidate output.
\item \textbf{Invalid output}: a structured candidate reaches verification but fails the plugin validator.
\item \textbf{Late submission}: a submission arrives after the relevant lease authority has expired.
\end{itemize}
The suite also injects task-specific factorization failures: invalid factors, false no-factor claims, raw-only model output, expired lease recovery, and no-factor recheck budget exhaustion.
}

\subsection{Task State and Idempotent Work Units}

{\color{blue}
TokenShare separates task, lease, and attempt state. A \texttt{TaskUnit} records coarse lifecycle state and dependency readiness. A \texttt{Lease} records authority to work on a unit for a bounded interval. An \texttt{Attempt} records execution progress and the submission/verification/canonical path. Idempotence is enforced at the event boundary: retries must either match the same logical fact or be recorded as distinct evidence rather than overwriting prior state.
}

\subsection{Lifecycle State Machine}

{\color{blue}
The implemented lifecycle uses three state machines:
\[
\begin{aligned}
\mathrm{TaskUnit}:&\quad
\textsc{Created}\rightarrow\textsc{Ready}\rightarrow\textsc{Processing}\rightarrow\textsc{Completed},\\
\mathrm{Lease}:&\quad
\textsc{Active}\rightarrow\{\textsc{Released},\textsc{Expired},\textsc{Revoked}\},\\
\mathrm{Attempt}:&\quad
\textsc{Created}\rightarrow\textsc{Running}\rightarrow\textsc{Submitted}\rightarrow
\{\textsc{Verified},\textsc{Rejected}\}\rightarrow\textsc{Canonical}.
\end{aligned}
\]
This split prevents a timeout from being confused with output rejection, and prevents a verified but non-canonical attempt from being treated as completed work.
}

\subsection{Failure Detection}

{\color{blue}
Failure detection is currently ledger-driven. Heartbeats extend evidence of lease activity; lease expiry returns the unit to a schedulable state when retry policy allows; executor errors and parse failures are persisted as artifacts or submissions; invalid outputs are rejected by verification reports. The important property is that each failure is observed at a named boundary, so later metrics can attribute the recovery to parser, verifier, lease, budget, or merge behavior.
}

\subsection{Adaptive Redundant Assignment}

{\color{blue}
The prototype focuses on mechanism necessity rather than adaptive redundancy. Experiment~3 disables one boundary at a time: verification, parser policy, requeue, all-required merge gate, and slot-integrity checking. The resulting degradations show why redundancy alone would be insufficient: if malformed raw output can bypass parsing or if a merge can ignore missing slots, additional attempts only produce more untrusted evidence.
}

\subsection{\textcolor{blue}{Straggler Mitigation and Lease Recovery}}

{\color{blue}
The current recovery path is lease-based. A unit with an expired lease can be requeued, while prior attempts and artifacts remain in the ledger for audit. In the experiments, worker-crash recovery is demonstrated by preserving the failed evidence and completing through a later valid attempt. This ties the recovery claim to implemented lease, retry, and audit machinery.
}

\subsection{\textcolor{blue}{Verification Boundaries}}

{\color{blue}
Verification is currently performed at explicit protocol boundaries and delegated to deterministic plugin validators. This is a strength of the two proof-of-concept applications: factorization provides arithmetic recheck, and Lean provides an external proof checker. The protocol records verification reports in a form that preserves validator identity, inputs, outputs, logs, and acceptance status, so the reported experiments can be audited through domain-specific evidence rather than informal agreement.
}

\subsection{Semantic Quality Aggregation}

{\color{blue}
Semantic quality aggregation is not used as experimental evidence in this paper. Its relevance is architectural: TokenShare's parser, verification-report, canonical-selection, and artifact interfaces could host probabilistic or review-based validators for future weak-verification domains. The present evaluation deliberately uses tasks with checkable acceptance conditions so that protocol failures cannot be hidden behind subjective quality scores.
}

\subsection{\textcolor{blue}{Contribution Eligibility and Delayed Settlement}}

{\color{blue}
The implemented accounting layer records contribution eligibility after canonical completion, accepted expansion, or accepted merge. Settlement is delayed until the root completion path can identify the complete eligible contribution set. This is sufficient for the paper's mechanism claim: accounting is derived from accepted protocol facts, not from executor self-reporting.
}

\subsection{Dispute Resolution}

{\color{blue}
Dispute resolution appears in the prototype as boundary rejection rather than a separate adjudication workflow. The useful pattern is:
\begin{enumerate}
\item \textbf{Parse isolation}: raw-only or malformed output produces a parse-failure artifact.
\item \textbf{Verification rejection}: structured but wrong output produces a rejected verification report.
\item \textbf{Canonical exclusion}: verified losers remain evidence but do not bind canonical state.
\item \textbf{Merge blocking}: incomplete or slot-inconsistent child output sets do not complete the parent.
\end{enumerate}
These outcomes are enough to explain why invalid evidence remains visible without becoming accepted evidence.
}

\subsection{Control-Plane Fault Tolerance}

{\color{blue}
The control plane is event-sourced. Task graph changes, leases, attempts, requests, submissions, verification reports, canonical bindings, expansion batches, merge records, contribution records, and settlement records are stored as append-only events and artifact references. This gives the prototype three properties:
\begin{itemize}
\item \textbf{Recoverability}: materialized views are rebuilt from event and artifact evidence.
\item \textbf{No double accounting}: root settlement is a batch fact over a complete eligible contribution set.
\item \textbf{Auditable provenance}: accepted outputs link back to requests, submissions, checker evidence, merge records, and environment or provider metadata.
\end{itemize}
}

\subsection{Fault-Tolerance Summary}

{\color{blue}
TokenShare's fault-tolerance claim is therefore narrow and testable: failures may produce extra events, rejected artifacts, parse-failure reports, expired leases, or inconclusive ablation runs, but they should not silently alter canonical output. The reported experiments evaluate precisely this property, including an ablation case where removing verification creates canonical pollution and thereby demonstrates the necessity of the boundary.
}
\section{Proof of Concept Applications}



{\color{blue}
The two applications instantiate the same protocol skeleton but stress different properties. The factorization plugin is a clean arithmetic workload with cheap deterministic verification and strict all-required merge slots. The Lean proof plugin is a formal-verification workload with a fixed local checker, proof artifacts, environment references, and split/merge proof evidence. Figure~\ref{fig:poc_workflow} summarizes the common protocol loop used by both applications.
}

{
\begin{figure}[t]
\centering
\resizebox{\linewidth}{!}{%
\begin{tikzpicture}[
  node distance=1.15cm,
  box/.style={draw, rounded corners, align=center, minimum width=2.5cm, minimum height=0.9cm, font=\small},
  smallbox/.style={draw, rounded corners, align=center, minimum width=2.2cm, minimum height=0.8cm, font=\small},
  arrow/.style={-Latex, thick}
]
\node[box] (bench) {Benchmark\\instances};
\node[box, right=of bench] (register) {Register\\root task};
\node[box, right=of register] (decompose) {\textcolor{blue}{Plugin split}\\\textcolor{blue}{or complete}};
\node[box, right=of decompose] (lease) {\textcolor{blue}{Lease ready}\\\textcolor{blue}{units}};
\node[box, below=of lease] (execute) {\textcolor{blue}{Executor}\\\textcolor{blue}{request path}};
\node[box, left=of execute] (submit) {\textcolor{blue}{Submission}\\\textcolor{blue}{artifacts}};
\node[box, left=of submit] (verify) {\textcolor{blue}{Parser + plugin}\\\textcolor{blue}{verification}};
\node[box, left=of verify] (merge) {\textcolor{blue}{Canonical}\\\textcolor{blue}{or merge}};
\node[box, below=of verify] (settle) {\textcolor{blue}{Contribution}\\\textcolor{blue}{accounting}};

\draw[arrow] (bench) -- (register);
\draw[arrow] (register) -- (decompose);
\draw[arrow] (decompose) -- (lease);
\draw[arrow] (lease) -- (execute);
\draw[arrow] (execute) -- (submit);
\draw[arrow] (submit) -- (verify);
\draw[arrow] (verify) -- node[above, font=\scriptsize] {accepted} (merge);
\draw[arrow] (merge) -- (settle);
\draw[arrow] (verify.north) to[out=90,in=270] node[above, font=\scriptsize] {\textcolor{blue}{rejected or expired}} (decompose.south);
\draw[arrow] (merge.north) to[out=90,in=270] node[above, font=\scriptsize] {\textcolor{blue}{required slot missing}} (decompose.south);
\end{tikzpicture}}
\caption{\textcolor{blue}{Common proof-of-concept workflow. Each benchmark instance is registered as a root task, optionally expanded by a plugin-owned split strategy, executed through an executor boundary, verified by a task-specific checker, and recorded through canonical, merge, contribution, and settlement events.}}
\label{fig:poc_workflow}
\end{figure}

\begin{table}[t]
\caption{How the two applications instantiate TokenShare.}
\label{tab:poc_applications}
\centering
\small
\begin{tabularx}{\linewidth}{p{0.18\linewidth}XX}
\toprule
Component & Large integer factorization & Lean formal proof production \\
\midrule
\textcolor{blue}{Root task} & \textcolor{blue}{Factor a small integer fixture, including prime and semiprime cases.} & \textcolor{blue}{Check a structured Lean theorem payload under fixed imports and environment $\Omega$.} \\
\textcolor{blue}{Task unit} & \textcolor{blue}{\texttt{root}, \texttt{factor\_integer}, \texttt{factor\_search\_range}, or \texttt{factorization\_merge}.} & \textcolor{blue}{Root theorem, child theorem, or merge-proof unit.} \\
\textcolor{blue}{Decomposition} & \textcolor{blue}{\texttt{candidate\_range\_partition.v1} covers $[2,\lfloor\sqrt n\rfloor]$ with required range slots.} & \textcolor{blue}{Lean-side deterministic split helper emits certificate-backed child goals and merge skeletons.} \\
\textcolor{blue}{Submission} & \textcolor{blue}{Structured range-result artifact or parser-failure evidence from raw output.} & \textcolor{blue}{Schema-bound proof candidate, checker report, proof artifact, and environment evidence.} \\
\textcolor{blue}{Verifier} & \textcolor{blue}{Deterministic arithmetic recheck and all-required merge policy.} & \textcolor{blue}{Fixed local Lean/lake checker with persisted stdout, stderr, generated source, and \texttt{EnvironmentRef}.} \\
\textcolor{blue}{Recovery} & \textcolor{blue}{Parser isolation, invalid-output rejection, expired lease requeue, and merge blocking.} & \textcolor{blue}{Rejected proof candidates remain evidence; accepted child proofs feed a checker-validated merge proof.} \\
\textcolor{blue}{Main metrics} & \textcolor{blue}{Final correctness, canonical pollution, completion, settlement, event count, artifact count.} & \textcolor{blue}{Real checker evidence, environment completeness, decomposition/merge lifecycle coverage.} \\
\bottomrule
\end{tabularx}
\end{table}


\subsection{Application I: Large Integer Factorization}

{\color{blue}
The first proof-of-concept application is the \texttt{factorization@0.1.0} plugin. Its role is not to compete with specialized number-theory software; it supplies a compact workload in which the protocol can observe typed decomposition, bounded execution, deterministic verification, all-required merge, contribution accounting, and canonical-state safety.
}

\paragraph{Task specification.}
{\color{blue}
The registered task is
\[
\mathcal{S}_{\mathrm{fac}}=(n,\mathrm{requested\_output},\mathrm{params},\mathrm{plugin\_version}),
\]
where $n$ is stored as a decimal string and the requested output is a prime factorization result. A range child accepts only \texttt{factorization.range\_result.v1}. The core arithmetic check is
\[
V_{\mathrm{fac}}(n,d)=
\begin{cases}
1, & \text{if } 1<d<n \text{ and } n\bmod d=0,\\
0, & \text{otherwise}.
\end{cases}
\]
and no-factor claims are also rechecked against their assigned closed interval. The plugin merge policy emits a final \texttt{PrimeFactorizationResult} only when the required evidence is complete.
}

\paragraph{Decomposition.}
{\color{blue}
The plugin split strategy partitions the candidate divisor interval $[2,\lfloor \sqrt{n}\rfloor]$ into ranges
\[
I_j=[a_j,b_j],
\]
with a coverage proof showing no gaps and no overlaps. Each range unit receives a bounded instruction:
\[
u_j=(n,[a_j,b_j],\mathrm{coverage\_id},\mathrm{child\_index}).
\]
The executor may search only inside that interval and may not create child tasks, invent output schemas, or claim the final factorization.
}

\paragraph{Experimental workflow.}
{\color{blue}
Experiment~1 runs small-prime, prime-range, semiprime-range, and extended semiprime fixture cases. Experiment~2 injects invalid factor, false no-factor, raw-only parse failure, expired lease, and verification-budget failures. Experiment~3 disables one boundary per run to show controlled degradation.
}

\paragraph{Baselines and metrics.}
{\color{blue}
The primary baseline is not a faster factorization algorithm but the same fixture lifecycle with selected protocol boundaries removed. Metrics therefore focus on final correctness, completion rate, canonical pollution, settlement success, event footprint, and artifact footprint.
}


\subsection{Application II: Lean Formal Proof Production}

{\color{blue}
The second proof-of-concept application is the \texttt{lean\_proof@0.1.0} plugin. Lean supplies a high-value verification boundary: a proof artifact is accepted only if a fixed local Lean/lake environment checks it and the resulting checker evidence is persisted. This makes Lean a strong test for whether TokenShare can coordinate a domain whose correctness is external to the protocol core.
}

\paragraph{Task specification.}
{\color{blue}
The registered task is
\[
\mathcal{S}_{\mathrm{Lean}}=(s,\mathcal{I},\Omega,\Pi),
\]
where $s$ is a structured theorem statement, $\mathcal{I}$ is the allowed import set, $\Omega$ is the fixed Lean/lake environment, and $\Pi$ is the decomposition policy. A proof candidate must bind to the theorem payload digest. The checker predicate is
\[
V_{\mathrm{Lean}}(s,y,\Omega)=
\begin{cases}
1, & \text{if the project builds successfully in } \Omega,\\
0, & \text{otherwise}.
\end{cases}
\]
and an accepted report must include logs, generated source, proof artifact, and \texttt{EnvironmentRef}.
}

\paragraph{Recursive decomposition.}
{\color{blue}
Each Lean task unit is represented by a structured theorem payload rather than a natural-language goal. Direct proof and decomposition/merge paths are both supported in the fixture suite. A decomposition result is accepted only if the Lean-side helper emits a supported split certificate:
\[
u=(s,\mathcal{I},\Omega,\mathrm{payload\_digest},\Pi),
\]
and a proof candidate may enter the protocol only as one of the following artifact-backed forms:
\[
y_u \in \{\textsc{DirectProof}(p_u),\textsc{ChildProof}(p_i),\textsc{MergeProof}(p_{\mathrm{root}})\}.
\]
The merge policy reads accepted child proof artifacts, constructs a root merge proof, and invokes the checker again.
}

\paragraph{Experimental workflow.}
{\color{blue}
Experiment~4 runs a factorization semiprime lifecycle, a Lean direct proof fixture, and a Lean decomposition/merge fixture under the same experiment runner. The Lean adapter first performs a real preflight check, then reports checker evidence and environment completeness.
}


\paragraph{Recovery and settlement.}
{\color{blue}
Lean proof evidence enters the same accounting path as factorization evidence: accepted canonical proof artifacts and accepted merge facts can produce eligible contribution records, and root completion can trigger a sandbox settlement batch. Invalid proof candidates remain auditable checker evidence but do not bind canonical state.
}

\paragraph{Baselines and metrics.}
{\color{blue}
The Lean cases are evaluated by real checker evidence, environment-reference completeness, canonical pollution, event footprint, artifact footprint, and whether direct and decomposition/merge paths complete through the shared protocol lifecycle.
}



}
% Experiment section rewritten from committed outputs/experiments artifacts.
\begingroup
\color{blue}
\small
\renewcommand{\arraystretch}{1.12}
\providecommand{\FloatBarrier}{}
\providecommand{\TS}{TokenShare}
\providecommand{\tickyes}{\(\checkmark\)}
\providecommand{\tickno}{--}

\tikzset{
  tsbox/.style={draw=blue!70!black, fill=blue!6, rounded corners=2pt, line width=0.4pt},
  tsdarkbox/.style={draw=blue!70!black, fill=blue!18, rounded corners=2pt, line width=0.4pt},
  tsline/.style={draw=blue!70!black, line width=0.5pt},
  tsarrow/.style={draw=blue!70!black, -stealth, line width=0.6pt},
  tslabel/.style={font=\scriptsize, text=blue!75!black},
  tssmall/.style={font=\tiny, text=blue!75!black}
}

% Make caption labels such as "Figure 1:" and "Table 1:" blue as well.
% This avoids the common problem where only the caption body is blue but
% the automatically generated label remains black.
\makeatletter
\let\TSoldmakecaption\@makecaption
\renewcommand{\@makecaption}[2]{%
  \vskip\abovecaptionskip
  \sbox\@tempboxa{{\color{blue}\small #1: #2}}%
  \ifdim \wd\@tempboxa >\hsize
    {\color{blue}\small #1: #2\par}%
  \else
    \global\@minipagefalse
    \hb@xt@\hsize{\hfil\box\@tempboxa\hfil}%
  \fi
  \vskip\belowcaptionskip}
\makeatother

\section{Experiments}
\label{sec:experiments}

\subsection{Evaluation Objective}
\label{subsec:evaluation-objective}

The experiments evaluate \TS{} as a task-agnostic protocol layer for coordinating
plugin-owned decomposition, execution, verification, canonicalization, merge, and
accounting. The goal is not to introduce a new factorization algorithm or a new
theorem prover. Instead, the evaluation asks whether a shared protocol core can
coordinate heterogeneous contributors and domain-specific plugins while
preserving correctness, auditability, and recovery under failure.

We organize the evaluation into four experiments. Experiment~1 tests whether a
real factorization plugin can complete a full protocol lifecycle. Experiment~2
injects invalid or incomplete submissions to test whether canonical state remains
clean. Experiment~3 disables individual protocol protections to test whether
these mechanisms are necessary. Experiment~4 tests cross-plugin generality with
factorization and Lean proof workloads. We then report an auxiliary
contributor-heterogeneity simulation. This auxiliary study is not counted as an
additional experiment; it approximates a multi-user setting by comparing local,
model-backed, and malformed contributors on the same semiprime task.

\begin{table}[!htbp]
\centering
\caption{\textcolor{blue}{Evaluation groups and claims. The AI executor profile is treated as an auxiliary contributor-heterogeneity simulation rather than a separate experiment.}}
\label{tab:evaluation-groups}
\small
{\color{blue}
\begin{tabularx}{\linewidth}{p{0.17\linewidth}p{0.25\linewidth}X}
\toprule
Group & Workload & Primary claim \\
\midrule
Experiment 1 & Factorization lifecycle
& A real factorization plugin can complete decomposition, execution,
verification, canonical binding, merge, expected-output resolution,
contribution recording, and settlement. \\
Experiment 2 & Failure recovery
& Invalid factors, false no-factor claims, parse failures, crashes, and
verification-budget failures are isolated or recovered without canonical
pollution. \\
Experiment 3 & Mechanism ablation
& Removing verifier, parser policy, requeue, merge gate, or slot-integrity
checks produces observable degradation. \\
Experiment 4 & Cross-plugin generality
& The same protocol core coordinates factorization and Lean proof plugins while
preserving plugin-owned semantics. \\
Auxiliary simulation & Heterogeneous contributors
& Different contributor types are mediated by the same raw-output, parser,
verifier, artifact, and accounting boundary. \\
\bottomrule
\end{tabularx}
}
\end{table}

\subsection{Metrics and Status Definitions}
\label{subsec:metrics-status}

We report both task-level and protocol-level metrics. Task-level metrics include
final correctness, parser success rate, parsed output count, and parse failure
count. Protocol-level metrics include completion rate, canonical pollution count,
settlement success, real checker evidence, event count, artifact count, provider
attempts, retry count, token usage, cost estimate, and latency. We use
\emph{passed} for a run that satisfies the expected property, \emph{failed} for
an unexpected violation, \emph{blocked} for an unavailable runtime dependency,
and \emph{inconclusive} for an intentional ablation run in which disabling a
protection causes the expected degradation.

\subsection{Suite-Level Results}
\label{subsec:suite-level-results}

The default suite contains 17 runs. Twelve runs pass, five runs are expected
ablation degradations, and no run fails or becomes blocked. The five
inconclusive cases correspond to mechanism ablations; they are therefore
interpreted as evidence that removing protocol protections produces the predicted
degradation, not as unexpected implementation failures.

\begin{figure}[!htbp]
\centering
{\color{blue}
\begin{tikzpicture}[x=1cm,y=1cm]
  \node[tslabel, anchor=west] at (0,2.35) {Default suite status};

  % Main ribbon.
  % Total width = 12cm.
  % 17 runs total: 12 passed -> 8.47cm, 5 inconclusive -> 3.53cm.
  \draw[tsline] (0,1.40) rectangle (12,1.90);
  \fill[blue!22] (0,1.40) rectangle (8.47,1.90);
  \fill[blue!8]  (8.47,1.40) rectangle (12,1.90);
  \draw[tsline] (8.47,1.40) -- (8.47,1.90);

  \node[tslabel] at (4.24,1.65) {12 passed};
  \node[tslabel] at (10.24,1.65) {5 inconclusive};

  % Tick marks and labels.
  \draw[tsline] (0,1.28) -- (0,1.12);
  \draw[tsline] (8.47,1.28) -- (8.47,1.12);
  \draw[tsline] (12,1.28) -- (12,1.12);

  \node[tssmall, anchor=north] at (0,1.05) {0};
  \node[tssmall, anchor=north] at (8.47,1.05) {12};
  \node[tssmall, anchor=north] at (12,1.05) {17};

  % Summary cards, placed lower and separated.
  \node[tsbox, minimum width=2.7cm, minimum height=0.58cm] at (1.35,0.35) {Failed: 0};
  \node[tsbox, minimum width=2.7cm, minimum height=0.58cm] at (4.65,0.35) {Blocked: 0};
  \node[tsbox, minimum width=4.8cm, minimum height=0.58cm] at (9.10,0.35) {Ablation degradations: 5};
\end{tikzpicture}
}
\caption{\textcolor{blue}{Suite-level status ribbon. The default suite has 17 runs: 12 passed, 5 intentional ablation degradations, 0 failed, and 0 blocked.}}
\label{fig:suite-status-ribbon}
\end{figure}

\FloatBarrier

\subsection{Experiment 1: End-to-End Factorization Lifecycle}
\label{subsec:exp1-factorization}

Experiment~1 asks whether a real plugin can drive a complete \TS{} lifecycle.
The four cases cover direct completion, prime-range verification, semiprime
decomposition, and a larger semiprime benchmark. All four cases pass with final
correctness, completion rate 1.0, settlement success, and zero canonical
pollution. The key point is that the protocol records not only the final factors
but also lifecycle evidence: task expansion, child execution, verification,
canonical output binding, merge, and settlement.

\begin{table}[!htbp]
\centering
\caption{\textcolor{blue}{Experiment 1: factorization lifecycle results.}}
\label{tab:factorization-results}
\small
{\color{blue}
\begin{tabularx}{\linewidth}{p{0.10\linewidth}p{0.18\linewidth}p{0.14\linewidth}>{\centering\arraybackslash}p{0.10\linewidth}>{\centering\arraybackslash}p{0.10\linewidth}X}
\toprule
Case & Instance & Output & Events & Artifacts & Interpretation \\
\midrule
E1a & \(N=2\) & \([2]\) & 22 & 9
& Direct completion without range expansion. \\
E1b & \(N=97\) & \([97]\) & 96 & 38
& Prime case completed through bounded range verification. \\
E1c & \(N=91\) & \([7,13]\) & 96 & 38
& Semiprime case completed through range search and all-required merge. \\
E1d & \(N=8051\) & \([83,97]\) & 148 & 62
& Larger semiprime case exercised the same lifecycle at greater evidence depth. \\
\bottomrule
\end{tabularx}
}
\end{table}

\begin{figure}[!htbp]
\centering
{\color{blue}
\begin{tikzpicture}[x=0.085cm,y=0.82cm]
  \node[tslabel, anchor=west] at (0,4.85) {Evidence footprint by case};

  % axis
  \draw[tsline] (0,0) -- (160,0);
  \foreach \x/\lab in {0/0,40/40,80/80,120/120,160/160} {
    \draw[tsline] (\x,0.04) -- (\x,-0.04);
    \node[tssmall, anchor=north] at (\x,-0.08) {\lab};
  }
  \node[tssmall, anchor=west] at (162,0) {count};

  % rows: label, events, artifacts
  \foreach \y/\case/\ev/\art in {
    4/E1a/22/9,
    3/E1b/96/38,
    2/E1c/96/38,
    1/E1d/148/62
  }{
    \node[tslabel, anchor=east] at (-4,\y) {\case};
    \draw[blue!15, line width=4pt] (0,\y) -- (160,\y);
    \draw[blue!35, line width=4pt] (0,\y+0.08) -- (\ev,\y+0.08);
    \filldraw[draw=blue!70!black, fill=blue!35] (\ev,\y+0.08) circle (2.2pt);
    \node[tssmall, anchor=west] at (\ev+3,\y+0.08) {events \ev};

    \draw[blue!20, line width=4pt] (0,\y-0.12) -- (\art,\y-0.12);
    \filldraw[draw=blue!70!black, fill=blue!10] (\art,\y-0.12) circle (2pt);
    \node[tssmall, anchor=west] at (\art+3,\y-0.12) {artifacts \art};
  }
\end{tikzpicture}
}
\caption{\textcolor{blue}{Lollipop-style evidence footprint for Experiment~1. E1d produces the largest event and artifact footprint, while all four cases preserve final correctness and zero canonical pollution.}}
\label{fig:factorization-lollipop}
\end{figure}

The semiprime cases are the most informative because they require multiple child
range results, verified canonical bindings, and a plugin-owned merge rule. The
results support the claim that the protocol core coordinates the lifecycle while
factorization arithmetic remains plugin-owned.

\FloatBarrier

\subsection{Experiment 2: Failure Injection and Recovery}
\label{subsec:exp2-failure}

Experiment~2 evaluates whether invalid executor behavior can corrupt protocol
state. Each case injects a different failure mode: an invalid factor, a false
no-factor claim, an unparsable raw output, a worker crash or expired lease, and
an over-budget no-factor recheck. All five cases pass with final correctness,
completion rate 1.0, settlement success, and zero canonical pollution. Rather
than viewing the output as a final numerical answer alone, this experiment
inspects whether the protocol accepts, rejects, requeues, or isolates evidence at
the correct boundary.

\begin{figure}[!htbp]
\centering
{\color{blue}
\resizebox{0.92\linewidth}{!}{%
\begin{tikzpicture}[
  font=\scriptsize,
  rowlabel/.style={
    text=blue!75!black,
    anchor=east
  },
  faultlabel/.style={
    text=blue!75!black,
    anchor=west
  },
  header/.style={
    text=blue!75!black,
    align=center
  },
  cell/.style={
    draw=blue!55!black,
    fill=blue!3,
    rounded corners=1.5pt,
    line width=0.35pt,
    minimum width=1.15cm,
    minimum height=0.48cm,
    align=center
  },
  hitcell/.style={
    draw=blue!70!black,
    fill=blue!14,
    rounded corners=1.5pt,
    line width=0.45pt,
    minimum width=1.15cm,
    minimum height=0.48cm,
    align=center
  }
]

% Title
\node[
  font=\scriptsize,
  text=blue!75!black,
  anchor=west
] at (-5.4,3.55)
{Fault handling matrix};

% Column headers
\node[header] at (-0.4,2.85) {Parser};
\node[header] at (1.15,2.85) {Verifier};
\node[header] at (2.70,2.85) {Lease};
\node[header] at (4.25,2.85) {Budget};
\node[header, text width=1.65cm] at (5.95,2.85) {Canonical\\clean};

% ---------------- Row E2a ----------------
\node[rowlabel] at (-5.0,2.15) {E2a};
\node[faultlabel] at (-4.65,2.15) {Invalid factor};

\node[cell] at (-0.4,2.15) {};
\node[hitcell] at (1.15,2.15) {\(\checkmark\)};
\node[cell] at (2.70,2.15) {};
\node[cell] at (4.25,2.15) {};
\node[hitcell] at (5.95,2.15) {\(\checkmark\)};

% ---------------- Row E2b ----------------
\node[rowlabel] at (-5.0,1.45) {E2b};
\node[faultlabel] at (-4.65,1.45) {False no-factor};

\node[cell] at (-0.4,1.45) {};
\node[hitcell] at (1.15,1.45) {\(\checkmark\)};
\node[cell] at (2.70,1.45) {};
\node[cell] at (4.25,1.45) {};
\node[hitcell] at (5.95,1.45) {\(\checkmark\)};

% ---------------- Row E2c ----------------
\node[rowlabel] at (-5.0,0.75) {E2c};
\node[faultlabel] at (-4.65,0.75) {Raw-only output};

\node[hitcell] at (-0.4,0.75) {\(\checkmark\)};
\node[cell] at (1.15,0.75) {};
\node[cell] at (2.70,0.75) {};
\node[cell] at (4.25,0.75) {};
\node[hitcell] at (5.95,0.75) {\(\checkmark\)};

% ---------------- Row E2d ----------------
\node[rowlabel] at (-5.0,0.05) {E2d};
\node[faultlabel] at (-4.65,0.05) {Worker crash};

\node[cell] at (-0.4,0.05) {};
\node[cell] at (1.15,0.05) {};
\node[hitcell] at (2.70,0.05) {\(\checkmark\)};
\node[cell] at (4.25,0.05) {};
\node[hitcell] at (5.95,0.05) {\(\checkmark\)};

% ---------------- Row E2e ----------------
\node[rowlabel] at (-5.0,-0.65) {E2e};
\node[faultlabel] at (-4.65,-0.65) {Budget exceeded};

\node[cell] at (-0.4,-0.65) {};
\node[cell] at (1.15,-0.65) {};
\node[cell] at (2.70,-0.65) {};
\node[hitcell] at (4.25,-0.65) {\(\checkmark\)};
\node[hitcell] at (5.95,-0.65) {\(\checkmark\)};

% Bottom note
\node[
  font=\scriptsize,
  text=blue!75!black,
  align=center,
  text width=10.8cm
] at (0,-1.55)
{\(\checkmark\) marks the boundary primarily responsible for rejecting,
recovering, or isolating the injected fault.};

\end{tikzpicture}
}
}
\caption{\textcolor{blue}{Failure-handling matrix for Experiment~2. Each injected failure is handled by the relevant protocol boundary, and every case preserves zero canonical pollution.}}
\label{fig:failure-handling-matrix}
\end{figure}

These results show that executor submission is not equivalent to protocol
acceptance. A candidate output must pass the parser, verifier, and
canonical-selection boundary before it can affect accepted state. Invalid
evidence may remain auditable, but it does not become canonical evidence.

\FloatBarrier

\subsection{Experiment 3: Mechanism Ablation}
\label{subsec:exp3-ablation}

Experiment~3 disables one protection mechanism per run. The expected outcome is
not ordinary completion but controlled degradation. All five ablations are
reported as inconclusive, with completion rate 0.0 and no settlement. The
verifier ablation additionally produces one canonical pollution event, showing
the direct risk of bypassing plugin verification.

\begin{figure}[!htbp]
\centering
{\color{blue}
\begin{tikzpicture}[x=1.05cm,y=0.72cm]
  \node[tslabel, anchor=west] at (0,6.1) {Ablation outcome heatmap};

  \node[tssmall] at (4.1,5.35) {Completion};
  \node[tssmall] at (5.9,5.35) {Settlement};
  \node[tssmall] at (7.6,5.35) {Pollution};
  \node[tssmall] at (9.4,5.35) {Risk signal};

  \foreach \row/\case/\removed/\comp/\settle/\poll/\risk in {
    4.6/E3a/Verifier/0/0/1/Canonical,
    3.8/E3b/Parser policy/0/0/0/Raw boundary,
    3.0/E3c/Requeue/0/0/0/Stuck work,
    2.2/E3d/Merge gate/0/0/0/Premature merge,
    1.4/E3e/Slot check/0/0/0/Wrong slot
  }{
    \node[tslabel, anchor=east] at (1.1,\row) {\case};
    \node[tssmall, anchor=west] at (1.25,\row) {\removed};

    \node[tsbox, minimum width=0.7cm, minimum height=0.40cm] at (4.1,\row) {0.0};
    \node[tsbox, minimum width=0.7cm, minimum height=0.40cm] at (5.9,\row) {no};

    \ifnum\poll=1
      \node[tsdarkbox, minimum width=0.7cm, minimum height=0.40cm] at (7.6,\row) {1};
    \else
      \node[tsbox, minimum width=0.7cm, minimum height=0.40cm] at (7.6,\row) {0};
    \fi

    \node[tsbox, minimum width=2.45cm, minimum height=0.40cm] at (9.4,\row) {\risk};
  }

  \node[tssmall, anchor=west] at (0.8,0.45)
  {All ablations are inconclusive by design; E3a directly shows canonical pollution when verification is removed.};
\end{tikzpicture}
}
\caption{\textcolor{blue}{Mechanism-ablation heatmap. Removing core protections prevents normal completion; removing verification additionally creates canonical pollution.}}
\label{fig:ablation-heatmap}
\end{figure}

The ablation suite supports a mechanism-level claim: correctness is not a
property of the task solver alone, but of the solver together with parser
ownership, verification, lease recovery, merge gating, and slot integrity.

\FloatBarrier

\subsection{Experiment 4: Cross-Plugin Generality}
\label{subsec:exp4-cross-plugin}

Experiment~4 tests whether the protocol core can coordinate plugins with
different semantics. The factorization case and both Lean proof cases pass. The
Lean cases include real checker evidence, and the decomposition/merge case tests
a split-and-merge proof path rather than only a direct proof.

\begin{figure}[!htbp]
\centering
{\color{blue}
\resizebox{0.92\linewidth}{!}{%
\begin{tikzpicture}[
  font=\scriptsize,
  box/.style={
    draw=blue!70!black,
    fill=blue!4,
    rounded corners=2pt,
    line width=0.5pt,
    align=center,
    inner sep=5pt
  },
  corebox/.style={
    draw=blue!70!black,
    fill=blue!14,
    rounded corners=2pt,
    line width=0.6pt,
    align=center,
    inner sep=6pt
  },
  arrow/.style={
    draw=blue!70!black,
    -stealth,
    line width=0.6pt
  }
]

% Top core box
\node[corebox, text width=10.5cm, minimum height=0.75cm] (core) at (0,3.2)
{\textbf{Shared TokenShare protocol core}};

% Three case cards
\node[box, text width=3.0cm, minimum height=2.25cm] (e4a) at (-4.2,1.0)
{\textbf{E4a}\\[3pt]
Factorization\\
semiprime lifecycle\\[5pt]
96 events\\
38 artifacts};

\node[box, text width=3.0cm, minimum height=2.25cm] (e4b) at (0,1.0)
{\textbf{E4b}\\[3pt]
Lean direct proof\\[5pt]
real checker\\
22 events\\
15 artifacts};

\node[box, text width=3.0cm, minimum height=2.25cm] (e4c) at (4.2,1.0)
{\textbf{E4c}\\[3pt]
Lean decomposition\\
and merge\\[5pt]
real checker\\
70 events\\
45 artifacts};

% Plugin labels
\node[font=\scriptsize, text=blue!75!black] at (-4.2,-0.55)
{factorization plugin};

\node[font=\scriptsize, text=blue!75!black] at (2.1,-0.55)
{lean proof plugin};

% Arrows from core to cases
\draw[arrow] (core.south west) -- (e4a.north);
\draw[arrow] (core.south) -- (e4b.north);
\draw[arrow] (core.south east) -- (e4c.north);

% Bottom note
\node[
  font=\scriptsize,
  text=blue!75!black,
  align=center,
  text width=10.5cm
] at (0,-1.35)
{All cases share the same lifecycle record: artifacts, verification reports,
canonical bindings, and settlement.};

\end{tikzpicture}
}
}
\caption{\textcolor{blue}{Cross-plugin generality in Experiment~4. The same protocol core supports both factorization and Lean proof plugins while domain semantics remain plugin-owned.}}
\label{fig:cross-plugin-map}
\end{figure}

\begin{table}[!htbp]
\centering
\caption{\textcolor{blue}{Experiment 4: cross-plugin generality results.}}
\label{tab:cross-plugin-results}
\footnotesize
{\color{blue}
\begin{tabularx}{0.96\linewidth}{
  @{}
  >{\raggedright\arraybackslash}p{0.10\linewidth}
  >{\raggedright\arraybackslash}p{0.24\linewidth}
  >{\raggedright\arraybackslash}p{0.22\linewidth}
  >{\raggedright\arraybackslash}X
  @{}
}
\toprule
Case & Workload and plugin & Evidence footprint & Interpretation \\
\midrule

E4a
&
\begin{minipage}[t]{\linewidth}
\textbf{Semiprime lifecycle}

Plugin: factorization
\end{minipage}
&
\begin{minipage}[t]{\linewidth}
Checker evidence: no

Events: 96

Artifacts: 38
\end{minipage}
&
\begin{minipage}[t]{\linewidth}
The arithmetic-search plugin completes the shared TokenShare lifecycle through plugin-owned factorization semantics.
\end{minipage}
\\[1.0em]

E4b
&
\begin{minipage}[t]{\linewidth}
\textbf{Lean direct proof}

Plugin: lean proof
\end{minipage}
&
\begin{minipage}[t]{\linewidth}
Checker evidence: yes

Events: 22

Artifacts: 15
\end{minipage}
&
\begin{minipage}[t]{\linewidth}
The direct proof path is accepted by a real Lean checker, showing that protocol acceptance can rely on external formal verification evidence.
\end{minipage}
\\[1.0em]

E4c
&
\begin{minipage}[t]{\linewidth}
\textbf{Lean decomposition and merge}

Plugin: lean proof
\end{minipage}
&
\begin{minipage}[t]{\linewidth}
Checker evidence: yes

Events: 70

Artifacts: 45
\end{minipage}
&
\begin{minipage}[t]{\linewidth}
The split child proofs and the merged root proof are accepted by the checker, demonstrating that the protocol can coordinate decomposition and merge beyond direct proof submission.
\end{minipage}
\\

\bottomrule
\end{tabularx}
}
\end{table}
The result supports the protocol generality claim. The core records lifecycle
state, artifacts, verification reports, canonical bindings, and settlement
records, while factorization arithmetic and Lean proof checking remain outside
the protocol core.

\FloatBarrier

\subsection{Auxiliary Simulation: Heterogeneous Contributors}
\label{subsec:aux-heterogeneous-contributors}

Because \TS{} studies heterogeneous execution resources, we include a contributor-
heterogeneity simulation. This simulation is not a fifth experiment. It
approximates a multi-user setting by running the same semiprime task under three
executor profiles: a deterministic local contributor, a real model-backed
contributor, and a malformed raw-output contributor. The workload is
\(N=91\), with expected factors \([7,13]\).

The simulation tests the executor boundary. A model-backed contributor may
produce raw outputs, but the protocol does not directly trust those outputs. Raw
responses must be stored, parsed into the factorization output contract, and
verified before they can become useful evidence. The malformed profile models an
unreliable contributor: its output is preserved as evidence, but it produces a
parse-failure artifact rather than an accepted parsed result.

\begin{figure}[!htbp]
\centering
{\color{blue}
\resizebox{0.92\linewidth}{!}{%
\begin{tikzpicture}[
  font=\scriptsize,
  box/.style={
    draw=blue!70!black,
    fill=blue!4,
    rounded corners=2pt,
    line width=0.5pt,
    align=center,
    inner sep=5pt
  },
  darkbox/.style={
    draw=blue!70!black,
    fill=blue!14,
    rounded corners=2pt,
    line width=0.6pt,
    align=center,
    inner sep=5pt
  },
  arrow/.style={
    draw=blue!70!black,
    -stealth,
    line width=0.6pt
  }
]

% Title
\node[font=\scriptsize, text=blue!75!black, anchor=west] at (-5.4,3.25)
{Executor boundary simulation};

% Row 1
\node[darkbox, text width=0.8cm, minimum height=0.75cm] (s1id) at (-4.6,1.9)
{\textbf{S1}};

\node[box, text width=2.8cm, minimum height=0.75cm] (s1type) at (-1.4,1.9)
{Deterministic local};

\node[box, text width=1.3cm, minimum height=0.75cm] (s1raw) at (1.7,1.9)
{raw: 0};

\node[box, text width=1.5cm, minimum height=0.75cm] (s1parsed) at (4.0,1.9)
{parsed: 4};

\node[box, text width=1.2cm, minimum height=0.75cm] (s1fail) at (6.1,1.9)
{fail: 0};

% Row 2
\node[darkbox, text width=0.8cm, minimum height=0.75cm] (s2id) at (-4.6,0.6)
{\textbf{S2}};

\node[box, text width=2.8cm, minimum height=0.75cm] (s2type) at (-1.4,0.6)
{Real model-backed};

\node[box, text width=1.3cm, minimum height=0.75cm] (s2raw) at (1.7,0.6)
{raw: 4};

\node[box, text width=1.5cm, minimum height=0.75cm] (s2parsed) at (4.0,0.6)
{parsed: 4};

\node[box, text width=1.2cm, minimum height=0.75cm] (s2fail) at (6.1,0.6)
{fail: 0};

% Row 3
\node[darkbox, text width=0.8cm, minimum height=0.75cm] (s3id) at (-4.6,-0.7)
{\textbf{S3}};

\node[box, text width=2.8cm, minimum height=0.75cm] (s3type) at (-1.4,-0.7)
{Malformed raw-output};

\node[box, text width=1.3cm, minimum height=0.75cm] (s3raw) at (1.7,-0.7)
{raw: 1};

\node[box, text width=1.5cm, minimum height=0.75cm] (s3parsed) at (4.0,-0.7)
{parsed: 0};

\node[darkbox, text width=1.2cm, minimum height=0.75cm] (s3fail) at (6.1,-0.7)
{fail: 1};

% Arrows row 1
\draw[arrow] (s1id.east) -- (s1type.west);
\draw[arrow] (s1type.east) -- (s1raw.west);
\draw[arrow] (s1raw.east) -- (s1parsed.west);
\draw[arrow] (s1parsed.east) -- (s1fail.west);

% Arrows row 2
\draw[arrow] (s2id.east) -- (s2type.west);
\draw[arrow] (s2type.east) -- (s2raw.west);
\draw[arrow] (s2raw.east) -- (s2parsed.west);
\draw[arrow] (s2parsed.east) -- (s2fail.west);

% Arrows row 3
\draw[arrow] (s3id.east) -- (s3type.west);
\draw[arrow] (s3type.east) -- (s3raw.west);
\draw[arrow] (s3raw.east) -- (s3parsed.west);
\draw[arrow] (s3parsed.east) -- (s3fail.west);

% Bottom note
\node[
  font=\scriptsize,
  text=blue!75!black,
  align=center,
  text width=10.4cm
] at (0.6,-2.05)
{Raw evidence becomes useful only after plugin-owned parsing and verification.};

\end{tikzpicture}
}
}
\caption{\textcolor{blue}{Executor-boundary outcomes in the contributor-heterogeneity simulation. The malformed contributor is recorded but not accepted.}}
\label{fig:executor-boundary-simulation}
\end{figure}

\begin{figure}[!htbp]
\centering
{\color{blue}
\resizebox{0.92\linewidth}{!}{%
\begin{tikzpicture}[
  font=\scriptsize,
  card/.style={
    draw=blue!70!black,
    fill=blue!4,
    rounded corners=2pt,
    line width=0.5pt,
    align=center,
    inner sep=6pt
  },
  darkcard/.style={
    draw=blue!70!black,
    fill=blue!14,
    rounded corners=2pt,
    line width=0.6pt,
    align=center,
    inner sep=6pt
  },
  metric/.style={
    draw=blue!55!black,
    fill=white,
    rounded corners=1.5pt,
    line width=0.4pt,
    align=center,
    inner sep=3pt
  }
]

% Title
\node[
  font=\scriptsize,
  text=blue!75!black,
  anchor=west
] at (-5.2,3.0)
{Cost--latency footprint of simulated contributors};

% -------------------------------------------------------------------
% S1 card
% -------------------------------------------------------------------
\node[card, text width=3.0cm, minimum height=3.0cm] (s1) at (-3.8,1.0)
{
  \textbf{S1}\\[2pt]
  Deterministic local\\[6pt]

  \begin{tabular}{c}
  latency: 0 ms\\
  cost: 0\\
  tokens: 0\\
  parsed: 4 / fail: 0
  \end{tabular}\\[5pt]

  \textit{baseline}
};

% -------------------------------------------------------------------
% S2 card
% -------------------------------------------------------------------
\node[darkcard, text width=3.2cm, minimum height=3.0cm] (s2) at (0,1.0)
{
  \textbf{S2}\\[2pt]
  Real model-backed\\[6pt]

  \begin{tabular}{c}
  latency: 49339 ms\\
  cost: 0.0041316\\
  tokens: 7457\\
  parsed: 4 / fail: 0
  \end{tabular}\\[5pt]

  \textit{accepted after parsing}
};

% -------------------------------------------------------------------
% S3 card
% -------------------------------------------------------------------
\node[card, text width=3.0cm, minimum height=3.0cm] (s3) at (3.8,1.0)
{
  \textbf{S3}\\[2pt]
  Malformed raw-output\\[6pt]

  \begin{tabular}{c}
  latency: 0 ms\\
  cost: 0.00006335\\
  tokens: 30\\
  parsed: 0 / fail: 1
  \end{tabular}\\[5pt]

  \textit{rejected by parser}
};

% Visual comparison strip
\node[
  metric,
  text width=2.7cm,
  minimum height=0.42cm
] at (-3.8,-1.25)
{no external cost};

\node[
  metric,
  fill=blue!10,
  text width=3.0cm,
  minimum height=0.42cm
] at (0,-1.25)
{highest cost and latency};

\node[
  metric,
  text width=2.7cm,
  minimum height=0.42cm
] at (3.8,-1.25)
{low cost, invalid output};

% Bottom explanation
\node[
  font=\scriptsize,
  text=blue!75!black,
  align=center,
  text width=10.6cm
] at (0,-2.05)
{The real model-backed contributor incurs external-resource overhead,
but its output is accepted only after plugin-owned parsing and verification.};

\end{tikzpicture}
}
}
\caption{\textcolor{blue}{Cost--latency footprint of simulated contributor profiles. The model-backed contributor increases cost and latency, while the malformed contributor remains cheap but produces no accepted parsed output.}}
\label{fig:cost-latency-footprint}
\end{figure}

The deterministic and real model-backed profiles have identical correctness and
parser success:
\[
  \Delta_{\mathrm{correctness}}=0,\qquad
  \Delta_{\mathrm{parser}}=0.0,\qquad
  \Delta_{\mathrm{retry}}=0.
\]
The real model-backed path introduces external-resource overhead in the explicit
\texttt{--real-transport} AI profile run reported in
\texttt{outputs/experiments/ai\_profile\_real\_fixed4}:
\[
  \Delta_{\mathrm{cost}}=0.0041316,\qquad
  \Delta_{\mathrm{latency}}=49339\ \mathrm{ms}.
\]
This simulation supports the resource-mediated interpretation of the protocol:
contributors may differ in execution medium, reliability, and cost, but their
outputs are mediated by a common parser, verifier, artifact, and accounting
interface.

\FloatBarrier

\subsection{Audit Footprint}
\label{subsec:audit-footprint}

The default suite records 1215 events and 510 artifacts. This footprint is not
only execution telemetry; it is the protocol evidence consumed by current
metrics and designed to support replay, audit, canonical-state inspection, and
contribution accounting.

\begin{figure}[!htbp]
\centering
{\color{blue}
\begin{tikzpicture}[x=0.0085cm,y=0.0042cm]
  \node[tslabel, anchor=west] at (0,1330) {Cumulative audit footprint};

  % axes
  \draw[tsline] (0,0) -- (1300,0);
  \draw[tsline] (0,0) -- (0,1250);

  \foreach \y/\lab in {0/0,400/400,800/800,1200/1200} {
    \draw[blue!15] (0,\y) -- (1250,\y);
    \node[tssmall, anchor=east] at (-30,\y) {\lab};
  }

  \foreach \x/\lab in {300/Exp.1,600/Exp.2,900/Exp.3,1200/Exp.4} {
    \draw[tsline] (\x,15) -- (\x,-15);
    \node[tssmall, anchor=north] at (\x,-40) {\lab};
  }

  % cumulative events
  \draw[blue!70!black, line width=0.9pt]
    (300,362) -- (600,842) -- (900,1027) -- (1200,1215);
  \foreach \x/\y in {300/362,600/842,900/1027,1200/1215}{
    \filldraw[draw=blue!70!black, fill=blue!35] (\x,\y) circle (3pt);
  }

  % cumulative artifacts
  \draw[blue!40!black, line width=0.9pt, dashed]
    (300,147) -- (600,337) -- (900,412) -- (1200,510);
  \foreach \x/\y in {300/147,600/337,900/412,1200/510}{
    \filldraw[draw=blue!40!black, fill=blue!8] (\x,\y) rectangle +(6,6);
  }

  \node[tssmall, anchor=west] at (850,1110) {cumulative events};
  \node[tssmall, anchor=west] at (850,455) {cumulative artifacts};
\end{tikzpicture}
}
\caption{\textcolor{blue}{Cumulative audit footprint across Experiments~1--4. The monotone increase reflects accumulated replay and artifact evidence, not merely final-answer records.}}
\label{fig:cumulative-audit-footprint}
\end{figure}

\begin{table}[!htbp]
\centering
\caption{\textcolor{blue}{Event and artifact footprint by experiment group.}}
\label{tab:audit-footprint}
\small
{\color{blue}
\begin{tabularx}{0.86\linewidth}{X>{\centering\arraybackslash}p{0.11\linewidth}>{\centering\arraybackslash}p{0.11\linewidth}>{\centering\arraybackslash}p{0.13\linewidth}>{\centering\arraybackslash}p{0.13\linewidth}}
\toprule
Group & Runs & Passed & Events & Artifacts \\
\midrule
Experiment 1 & 4 & 4 & 362 & 147 \\
Experiment 2 & 5 & 5 & 480 & 190 \\
Experiment 3 & 5 & 0 & 185 & 75 \\
Experiment 4 & 3 & 3 & 188 & 98 \\
\midrule
Total & 17 & 12 & 1215 & 510 \\
\bottomrule
\end{tabularx}
}
\end{table}

\FloatBarrier

\subsection{Limitations}
\label{subsec:limitations}

The results provide prototype-scale protocol evidence rather than a large-scale
performance benchmark. The factorization tasks are fixed small integers, the
default deterministic suite uses one seed, and the contributor-heterogeneity
simulation uses a small number of executor profiles rather than a large
population of real users. Accordingly, the evidence supports lifecycle
completeness, canonical-state safety, mechanism necessity, cross-plugin
execution, and AI-output auditability at the protocol-boundary level. Broader
throughput scaling, stronger adversarial workloads, richer replay tooling, and
multi-provider cost optimization remain separate evaluation targets.

\subsection{Summary}
\label{subsec:experiment-summary}

The experiments support four main conclusions. First, the factorization plugin
completes end-to-end lifecycle cases with correct outputs and settlement.
Second, injected failures do not pollute canonical state. Third, disabling key
mechanisms produces the expected degradation. Fourth, the same protocol core
supports factorization and real Lean proof plugins. The auxiliary contributor
simulation further shows how heterogeneous users or executors can be mediated by
the same raw-output, parser, verifier, artifact, and accounting boundary.

% Restore the original caption behavior and text color after this section.
\makeatletter
\let\@makecaption\TSoldmakecaption
\makeatother
\endgroup
\normalcolor



\section{Related Work}

\paragraph{Distributed task allocation and market coordination.}
{\color{blue}
TokenShare builds on a long line of work on allocating work among distributed agents. The Contract Net Protocol introduced a negotiation pattern in which tasks are announced, potential contractors bid, and managers award work to selected agents \citep{smith1980contract}. Multi-robot task allocation later formalized the relation among agents, tasks, utilities, costs, and assignment structure \citep{gerkey2004formal}, while market-based coordination studied how decentralized bidding mechanisms can trade off communication cost, robustness, and solution quality \citep{dias2006market}. These works justify treating executor selection, leases, and retry as protocol-visible allocation decisions. TokenShare differs in that the allocated object is not a single atomic job: it is a recursively expandable task tree or DAG whose leaves may require model calls, local tools, external checkers, or bounded compute, and whose contribution records become eligible only after parser, verifier, canonical-selection, and merge boundaries succeed.
}

\paragraph{Complex crowdsourcing and decentralized crowdsourcing.}
{\color{blue}
Human-computation systems show that complex work can be decomposed, distributed, reviewed, and recomposed. CrowdForge proposes partition, map, and reduce primitives for crowdsourcing complex work \citep{kittur2011crowdforge}, and Turkomatic explores recursive task and workflow design for Mechanical Turk-style settings \citep{kulkarni2011turkomatic}. Blockchain-based crowdsourcing systems such as CrowdBC and decentralized HIT protocols study payment, dispute handling, and reduced reliance on centralized platforms \citep{li2018crowdbc,liang2022decentralizedhit}. For TokenShare, the relevant lesson is that decomposition and review need durable protocol evidence. The prototype generalizes this lesson to heterogeneous intelligent work by making plugin schemas, artifact references, verification reports, canonical choices, and merge policies part of a reusable local protocol substrate rather than a fixed human-task workflow.
}

\paragraph{Volunteer and distributed execution systems.}
{\color{blue}
Volunteer and cluster-computing systems provide practical lessons for unreliable and heterogeneous execution. BOINC supports volunteer scientific computation over devices that differ in capability, availability, and reliability \citep{anderson2020boinc}. MapReduce popularized partitioned data processing with automatic scheduling, failure handling, and re-execution on commodity clusters \citep{dean2004mapreduce}. Ray supports dynamic task graphs for AI applications \citep{moritz2018ray}, while Sparrow studies decentralized low-latency scheduling for short parallel tasks \citep{ousterhout2013sparrow}. TokenShare adopts the engineering vocabulary of leases, heartbeats, re-execution, and reassignment, but applies it to semantic and verifiable intelligent production: a work unit must include an input schema, output schema, verifier, provenance record, and merge rule.
}

\paragraph{Blockchains, verifiable computation, and useful work.}
{\color{blue}
Bitcoin demonstrates that mutually untrusted participants can be coordinated through a public ledger and proof-of-work incentives \citep{nakamoto2008bitcoin}. Ethereum generalizes the ledger into programmable smart contracts for decentralized applications \citep{buterin2014ethereum}. TrueBit studies interactive verification for expensive off-chain computation \citep{teutsch2019truebit}. Proof-of-useful-work systems such as Ofelimos attempt to replace artificial hash puzzles with useful optimization work \citep{fitzi2022ofelimos}. This literature informs TokenShare's use of public commitments, verifiable evidence, and replayable state transitions. The prototype brings that evidence discipline into a local useful-work setting: append-only events, content-addressed artifacts, verification reports, and deterministic replay are used to study task lifecycles across plugins and executors.
}

\paragraph{LLM decomposition, tool use, and multi-agent workflows.}
{\color{blue}
Recent LLM research shows that complex reasoning benefits from explicit intermediate structure. Decomposed Prompting, Least-to-Most Prompting, Tree of Thoughts, and ReAct all externalize decomposition, search, tool use, or intermediate reasoning states \citep{khot2023decomposed,zhou2023least,yao2023tree,yao2023react}. HuggingGPT and related tool-use systems use an LLM to plan subtasks and route them to external models or tools \citep{shen2023hugginggpt}. Multi-agent frameworks such as CAMEL, AutoGen, MetaGPT, and ChatDev further introduce role specialization, agent communication, and structured software-production workflows \citep{li2023camel,wu2023autogen,hong2024metagpt,qian2023chatdev}. These works motivate TokenShare's use of decomposition, roles, and tool-facing agents. TokenShare complements them by making allocation, parser boundaries, verification reports, canonical selection, merge, and contribution provenance explicit protocol objects rather than hidden orchestration state.
}

\paragraph{Verification-heavy intelligent tasks.}
Formal proof assistants provide a useful testbed because accepted outputs can be checked deterministically. The Lean mathematical library shows how a large community can maintain formalized mathematics in Lean \citep{mathlib2020}. miniF2F provides a cross-system benchmark for formal olympiad-level mathematics \citep{zheng2021minif2f}, and LeanDojo exposes Lean proof states, premises, interaction data, and benchmarks for retrieval-augmented theorem proving \citep{yang2023leandojo}. These works support our Lean proof-production application: TokenShare can treat a theorem, subgoal, tactic patch, error log, or auxiliary lemma as a task unit, while Lean supplies a replayable verifier.

\paragraph{Annotation quality and low-resource public-good NLP.}
Crowdsourced annotation research provides mature models for noisy contributors and uncertain labels. Dawid--Skene style aggregation estimates latent labels and worker error rates \citep{dawid1979maximum}; GLAD models both annotator ability and item difficulty \citep{whitehill2009glad}; MACE estimates annotator competence under noisy or adversarial conditions \citep{hovy2013mace}; and Snorkel shows how weak supervision sources can be combined into probabilistic labels \citep{ratner2017snorkel}. Low-resource language work also warns that public-good NLP is not merely a data-scarcity problem: language technologies are unevenly distributed across the world's languages \citep{joshi2020state}, participatory projects such as Masakhane emphasize community involvement \citep{nekoto2020participatory}, and NLLB combines large-scale data construction with human-centered evaluation for many languages \citep{nllb2022}. These lines motivate TokenShare's emphasis on provenance, uncertainty, expert escalation, and community review rather than treating generated artifacts as automatically authoritative.





\begin{table}[t]
\centering
\small
\caption{Positioning of TokenShare relative to adjacent work.}
\label{tab:related_positioning}
\begin{tabularx}{\linewidth}{p{0.22\linewidth} X X}
\toprule
Line of work & Main contribution & Gap addressed by TokenShare \\
\midrule
Task allocation & Negotiated or market-based assignment among agents & \textcolor{blue}{Recursive task DAGs with verification-aware routing and contribution eligibility} \\
Complex crowdsourcing & Human workflow decomposition and recomposition & Heterogeneous LLM, tool, compute, and human contributors with typed verifiers \\
Distributed execution & Scheduling and recovery for unreliable machines & Semantic intelligent work units with provenance, audit, and merge rules \\
\textcolor{blue}{Ledgered verification} & \textcolor{blue}{Public commitments, verifiable evidence, and replayable state transitions} & \textcolor{blue}{Event-sourced evidence and replayable contribution accounting for useful-work lifecycles} \\
LLM-agent systems & Planning, tool use, role specialization, and agent communication & \textcolor{blue}{Fault tolerance, parser and verifier boundaries, contribution attribution, and protocol-level evidence} \\
\bottomrule
\end{tabularx}
\end{table}


\section{Conclusion}

{\color{blue}
This paper presented TokenShare, a replayable protocol kernel for decomposable and verifiable intelligent tasks. Instead of treating AI work as an isolated prompt-response event, TokenShare records the full lifecycle around useful work: typed task units, leases, execution attempts, artifacts, parser outcomes, verification reports, canonical bindings, expansion records, merge records, contribution records, and root-level accounting.

The core result is that a small local protocol kernel can support heterogeneous task semantics without absorbing them into the scheduler. In the evaluated prototype, factorization and Lean formal-proof plugins share the same lifecycle while retaining separate schemas, validators, split strategies, merge policies, and checker evidence. The default experiment suite further shows how failure injection, protocol ablation, cross-plugin generality, and an AI API executor can be studied through event and artifact evidence rather than final outputs alone.

The broader implication is that resource-mediated intelligent work can be made auditable at the protocol level. Future work should broaden benchmark scale, add richer replay and visualization tooling, test additional plugin families, and study resource-aware scheduling and accounting policies on top of the evidence-preserving kernel.
}


\section*{Ethical considerations}

{\color{blue}
The current experiments use arithmetic and formal-proof fixtures, but broader motivating domains such as annotation, knowledge organization, and low-resource language work can involve sensitive data, community knowledge, cultural context, and identity. Extending TokenShare to those settings requires licensing review, community consent, careful data governance, expert validation, minimal disclosure, and source-specific access control. Replayable provenance should support accountability while preserving uncertainty flags and avoiding overclaiming model-generated artifacts as community-authoritative without appropriate review.
}



\bibliographystyle{plainnat}
\bibliography{reference}

\end{document}
